\input{../../sheet.tex}
\sbasic
\input{../families/macros.tex}
\input{../natural_addition/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../objects/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../natural_difference/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../relations/macros.tex}
\input{../sentences/macros.tex}
\input{../function_composites/macros.tex}
\input{../direct_products/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_equality/macros.tex}
\input{../empty_set/macros.tex}
\input{../functions/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../sequences/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../real_sequences/macros.tex}
\input{../real_numbers/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../cardinality/macros.tex}
\input{../set_operations/macros.tex}
\input{../real_limits/macros.tex}
\input{../intervals/macros.tex}
\input{../measures/macros.tex}
\input{../extended_real_numbers/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Image Measures}

\ssection{Why}

A measurable
function from
a first measure space
to a second measurable space
induces a measure
on the latter.

\ssection{Definition}

Consider two measurable
spaces and a measurable
function between them.
The
\ct{image measure}{imagemeasure}
of a measure on the first space
\ct{under}{imagemeasureunder}
the measurable function
is the measure on the second space
which assigns to each measurable set
the measure of the inverse image of
that measurable set.

We say that the
function
\ct{induces}{}
the image measure
on the
codomain.
Alternatively,
we say that we
\ct{push forward}{}
the measure to the
codomain, and so
call the image
measure
a
\ct{push forward measure}{}.

\ssubsection{Notation}

Let
$(X, \mathcal{A})$
and
$(Y, \mathcal{B})$
be two measurable spaces.
Let $f: X \to Y$ be
a measurable function.
Let
$\mu: \mathcal{A} \to \nneri$
be a measure.
We denote the
image measure of $\mu$
under $f$ by
$\pushforward{\mu}{f}$,
for the reason that it
\[
  \pushforward{\mu}{f}(B) = \mu(f^{-1}(B))
\]
for every $B \in \mathcal{B}$.

\ssection{Change of Variables}

The main property
we would like to hold
is that integration
on the new measure space
is the same as integration
on the old.

\begin{prop}
  Let
  $(X, \mathcal{A})$
  and
  $(Y, \mathcal{B})$
  be measurable spaces
  and let $R$ denote
  the real numbers.
  Let $f: X \to Y$ be
  a measurable function
  and let
  $\mu: \mathcal{A} \to \nneri$
  be a measure.

  Then $g: Y \to R$
  is integrable with
  respect to
  $\pushforward{\mu}{f}$
  if and only if
  $g \circ f$
  is integrable with
  respect to
  $\mu$.
  In this case,
  \[
    \int g d(\pushforward{\mu}{f})
    =
    \int g \circ f d\mu.
  \]
  \begin{proof}
  \end{proof}
\end{prop}
\strats
