\input{../../sheet.tex}
\sbasic
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../objects/macros.tex}
\input{../sentences/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../relations/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../real_numbers/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_equality/macros.tex}
\input{../functions/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../intervals/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../set_operations/macros.tex}
\input{../real_functions/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../cardinality/macros.tex}
\input{../partitions/macros.tex}
\input{../characteristic_functions/macros.tex}
\input{../measures/macros.tex}
\input{../simple_functions/macros.tex}
\input{../measurable_functions/macros.tex}
\input{../simple_integrals/macros.tex}
\input{../nonnegative_integrals/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Real Integrals}

\ssection{Why}

We define the area under an extended real function.

\ssection{Definition}

The \t{positive part} of an extended-real-valued function is the function mapping each element to the maximum of the function's result and zero.
The \t{negative part} of an extended-real-valued function is the function mapping each element to the maximum of the additive inverse of function's result and zero.

We decompose an extended-real-valued function as the difference of its positive part and its negative part.
Both the positive and negative parts are non-negative extended-real-valued functions.

Consider a measure space.
An \t{integrable} function is a measurable extended real function for which the non-negative integral of the posititve part and the non-negative integral of the negative part of the function are finite.
The \t{integral} of an integrable function is the difference of the non-negative integral of the posititive part and and the non-negative integral of the negative part.

If one but not both of the parts of the function are finite, we say that the integral \t{exists} and again define it as before.
In this way we avoid arithmetic between two infinities.

\ssubsection{Notation}

Let $A$ a non-empty set.
Let $g: A \to [-\infty, \infty]$.
We denote the positive part
of $g$ by $g^+$ and the negative
part of $g$ by $g^-$:
\[
  g^+(x) = \max\set{g(x), 0} \quad \text{ and } \quad g^-(x) = \max\set{-g(x), 0}.
\]
Moreover, we decompose
$g$
as
$g = g^+ - g^-$.
We observed that
$g^+(x) \geq 0$ and
$g^-(x) \geq 0$
for all $x \in X$.

Let $(X, \mathcal{A}, \mu)$
be a measure space.
Let $f: X \to [-\infty, +\infty]$
measurable and
one of
$\int f^+ d \mu$ or
$\int f^- d \mu$
is finite
(if both are finite,
$f$ is integrable).

We denote the integral
of $f$ with respect to the
measure $\mu$ by
$\int f d \mu$.
We defined:
\[
  \int f d\mu = \left(\int f^+ d\mu\right) - \left(\int f^- d\mu\right).
\]
\strats
