%!name:tree-structured_distributions
%!need:conditional_distributions
%!need:rooted_trees

\ssection{Why}

\ssection{Definition}

\subsection{Rooted Definition}

Consider a set of outcomes which
is a direct product of $n$ sets.
Consider a distribution on this
set of outcomes.
The distribution has
$n$ marginals distributions.
The $n(n-1)$ conditionals
of each component given another.
Consider a rooted tree over $n$ vertices.

The distribution
\ct{factors according to the rooted tree}{}
if the probability for every outcome can
be written as a product
of the marginal probability of the outcome
at the root with the produce of the probabilities
of the conditionals correponding to the edges
in the tree.

\subsubsection{Notation}


Let $p$ be a distribution on
a $d$-dimensional space.
$p$
\ct{factors according to the rooted tree}{}
on $\set{1, \dots, d}$ rooted
at a vertex $k$ if it can be
written as a product of $p_k$
and the conditionals of $p_{i \mid j}$
for $i,j = 1, \dots, d$ and $i \neq j$
and $i \neq k$ where $j$ is the parent
of $i$ in the rooted tree.

\subsection{Defining Result}
\begin{prop}
If a distribution factors according
to a tree rooted at a vertex it
factors according to that tree rooted
at any vertex.
\end{prop}

\ssubsection{Undirected Definition}

A distribution $p$
\ct{factors according to the tree}{} $T$
if it factors according to the
$T$ rooted at any vertex.

\ssection{Existence and Uniqueness}

Trees are not a property of distributions,
since there is no one-to-one correspondence,
as demonstrated by the following propositions.

\ssubsection{Existence}

A distribution $p$ need not factor according to a tree.

\ssubsection{Uniqueness}
A distribution
$p$ may factor according to multiple trees.
