\input{../../sheet.tex}
\sbasic
\input{../conditional_distributions/macros.tex}
\input{../rooted_trees/macros.tex}
\input{../conditional_event_probability/macros.tex}
\input{../marginal_distributions/macros.tex}
\input{../probability_distributions/macros.tex}
\input{../trees/macros.tex}
\input{../event_probabilities/macros.tex}
\input{../direct_products/macros.tex}
\input{../probability_outcomes/macros.tex}
\input{../real_summation/macros.tex}
\input{../graphs/macros.tex}
\input{../probability_events/macros.tex}
\input{../set_operations/macros.tex}
\input{../natural_families/macros.tex}
\input{../natural_order/macros.tex}
\input{../cardinality/macros.tex}
\input{../probability/macros.tex}
\input{../natural_summation/macros.tex}
\input{../real_numbers/macros.tex}
\input{../relations/macros.tex}
\input{../subsets/macros.tex}
\input{../algebras/macros.tex}
\input{../families/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../common_sense/macros.tex}
\input{../arithmetic/macros.tex}
\input{../family_operations/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../sets/macros.tex}
\input{../operations/macros.tex}
\input{../functions/macros.tex}
\input{../set_specification/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../objects/macros.tex}
\input{../set_equality/macros.tex}
\input{../solving_equations/macros.tex}
\input{../identity/macros.tex}
\input{../equations/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Tree-Structured Distributions}

\ssection{Why}

\ssection{Definition}

\subsection{Rooted Definition}

Consider a set of outcomes which
is a direct product of $n$ sets.
Consider a distribution on this
set of outcomes.
The distribution has
$n$ marginals distributions.
The $n(n-1)$ conditionals
of each component given another.
Consider a rooted tree over $n$ vertices.

The distribution
\ct{factors according to the rooted tree}{}
if the probability for every outcome can
be written as a product
of the marginal probability of the outcome
at the root with the produce of the probabilities
of the conditionals correponding to the edges
in the tree.

\subsubsection{Notation}


Let $p$ be a distribution on
a $d$-dimensional space.
$p$
\ct{factors according to the rooted tree}{}
on $\set{1, \dots, d}$ rooted
at a vertex $k$ if it can be
written as a product of $p_k$
and the conditionals of $p_{i \mid j}$
for $i,j = 1, \dots, d$ and $i \neq j$
and $i \neq k$ where $j$ is the parent
of $i$ in the rooted tree.

\subsection{Defining Result}
\begin{prop}
If a distribution factors according
to a tree rooted at a vertex it
factors according to that tree rooted
at any vertex.
\end{prop}

\ssubsection{Undirected Definition}

A distribution $p$
\ct{factors according to the tree}{} $T$
if it factors according to the
$T$ rooted at any vertex.

\ssection{Existence and Uniqueness}

Trees are not a property of distributions,
since there is no one-to-one correspondence,
as demonstrated by the following propositions.

\ssubsection{Existence}

A distribution $p$ need not factor according to a tree.

\ssubsection{Uniqueness}
A distribution
$p$ may factor according to multiple trees.
\strats
