\input{../../sheet.tex}
\sbasic
\input{../objects/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../sentences/macros.tex}
\input{../set_equality/macros.tex}
\input{../equations/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../operations/macros.tex}
\input{../set_specification/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../algebras/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_intersections/macros.tex}
\input{../empty_set/macros.tex}
\input{../power_set/macros.tex}
\input{../functions/macros.tex}
\input{../zero/macros.tex}
\input{../relations/macros.tex}
\input{../family_operations/macros.tex}
\input{../common_sense/macros.tex}
\input{../injective_functions/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../natural_sums/macros.tex}
\input{../length_common_notions/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../partial_orders/macros.tex}
\input{../natural_summation/macros.tex}
\input{../probability/macros.tex}
\input{../cardinality/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../natural_differences/macros.tex}
\input{../distance/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../total_orders/macros.tex}
\input{../real_summation/macros.tex}
\input{../probability_outcomes/macros.tex}
\input{../intervals/macros.tex}
\input{../direct_products/macros.tex}
\input{../metrics/macros.tex}
\input{../real_numbers/macros.tex}
\input{../optimizers/macros.tex}
\input{../probability_distributions/macros.tex}
\input{../datasets/macros.tex}
\input{../similarity_functions/macros.tex}
\input{../real_optimizers/macros.tex}
\input{../empirical_distribution/macros.tex}
\input{../approximators/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Distribution Approximators}

\ssection{Why}

We have a distribution to approximate.
It is, for some reason, unsuitable to our needs and we want to replace it with one more suitable.

\ssection{Definition}

A \t{distribution approximator} is an approximator of a probability distribution.
It is also a distribution.
The criterion of approximation is any similarity function on distributions over the same space.

\ssection{Notation}

Let $A$ be a non-empty set and $q: A \to \R$ be a distribution.
Let $p: A \to \R$ be a distribution.
Then $p: A \to \R$ is a distribution approximator of $q$.

\ssection{Reasons for approximation}


\textbf{Infeasible to represent.}
If there are many outcomes, many numbers are required to specify the distribution.
If $p: A^n \to \R$ where $|A| = k$, then there are $k^n$ outcomes; take, for example, $k = 2$ and $n = 100$.
So we might want to find a distribution which requires fewer numbers to express.
In other words, we want a different distribution, selected from the set of those which is easier to express, which is close to the original.

\textbf{Unreasonable from common sense.}
The distribution may be unreasonable as a result of our common sense.
For example, it may give zero probability to an outcome which we know to be possible, and would like to model with non-zero probability.
This may happen when working with an empirical distribution: a particular outcome does not appear in the dataset, however, our common sense suggests is possible.
In this case, we want to find a different distribution, selected from the set of those which is more reasonable based on common sense, which is close to the original.
\strats
