%!name:distribution_approximators
%!need:approximators
%!need:empirical_distribution

\ssection{Why}

We have a distribution to approximate.
It is, for some reason, unsuitable to our needs and we want to replace it with one more suitable.

\ssection{Definition}

A \t{distribution approximator} is an approximator of a probability distribution.
It is also a distribution.
The criterion of approximation is any similarity function on distributions over the same space.

\ssection{Notation}

Let $A$ be a non-empty set and $q: A \to \R$ be a distribution.
Let $p: A \to \R$ be a distribution.
Then $p: A \to \R$ is a distribution approximator of $q$.

\ssection{Reasons for approximation}


\textbf{Infeasible to represent.}
If there are many outcomes, many numbers are required to specify the distribution.
If $p: A^n \to \R$ where $|A| = k$, then there are $k^n$ outcomes; take, for example, $k = 2$ and $n = 100$.
So we might want to find a distribution which requires fewer numbers to express.
In other words, we want a different distribution, selected from the set of those which is easier to express, which is close to the original.

\textbf{Unreasonable from common sense.}
The distribution may be unreasonable as a result of our common sense.
For example, it may give zero probability to an outcome which we know to be possible, and would like to model with non-zero probability.
This may happen when working with an empirical distribution: a particular outcome does not appear in the dataset, however, our common sense suggests is possible.
In this case, we want to find a different distribution, selected from the set of those which is more reasonable based on common sense, which is close to the original.
