\input{../../sheet.tex}
\sbasic
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../set_specification/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../set_unions/macros.tex}
\input{../graphs/macros.tex}
\input{../trees/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Rooted Trees}

\ssection{Why}

We want to talk about orienting the edges of a tree away from a given vertex.

\ssection{Definition}

A \t{rooted tree} is an ordered pair consisting of a tree and a distinguished vertex, which we call the \t{root}.
The \t{parent} of a given non-root vertex is the first vertex on the path from the given vertex to the root.
Conversely, that given vertex is the \t{child} of its parent.
Since there is only one path to the root, each non-root vertex has only one parent.
We define the parent of the root to be the root itself.

% We associate with a rooted tree the directed graph constructed by orienting al edges away from the root.
% For a particular rooted tree, which is to say a particular choice of root, we obtain a directed graph.
% There are many choices of root, and so naturally we wonder if each choice of root corresponds to a different directed graph.
% Since trees are connected, each choice of root does lead to a different graph.
% If they were disconnected, some of the graphs may turn out to be the same.
% So there is a one-to-one correspondence between rooted trees and their associated directed graphs, and so we could have defined a rooted tree as a directed graph with particular properties.
%
\ssubsection{Notation}

Let $T = (V, E)$ be a tree.
We denote the tree $T$ rooted at vertex $v$ by $(T, v)$.

\ssection{Properties}

\begin{prop}
Let $(T, v)$ be a rooted tree.
In the directed graph corresponding to this rooted tree every vertex has one parent.
\end{prop}

We denote the parent of vertex $v$ by $\pa{v}$.
\strats
