\input{../../sheet.tex}
\sbasic
\input{../objects/macros.tex}
\input{../identity/macros.tex}
\input{../sets/macros.tex}
\input{../set_equality/macros.tex}
\input{../sentences/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../empty_set/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../relations/macros.tex}
\input{../power_set/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../functions/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_operations/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../cardinality/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Sigma Algebras}

\ssection{Why}

For general measure theory,
we need an algebra of sets
closed under countable unions;
we define such an object (TODO).

\ssection{Definition}

A \ct{countably summable subset algebra}{sigmaalgebra}
is a subset space for which
(1) the base set is distinguished
(2) the complement of a distinguished
set is distinguished
(3) the union of a sequence of distinguished sets
is distinguished.

The name is justified, as
each countably summable subset algebra is a
\rt{subset algebra}{subsetalgebra},
because the union of $A_1, \dots, A_n$
coincides with the union of
$A_1, \dots, A_n, A_n, A_n \dots$.

We say that the set of distinguished
sets a \ct{sigma algebra}{sigmaalgebra} on the
base set; we justify this langauge, as for
an algebra, by the closure properties
under standard set operations.

\ssubsection{Notation}

The notation follows that of a subset space.
Let $(A, \mathcal{A})$ be a countably summable
subset algebra.
We also say \say{let $\mathcal{A}$ be
an sigma algebra on $A$.}
Moreover, since the largest element of the
sigma algebra is the base set, we can say without
ambiguity: \say{let $\mathcal{A}$ be a sigma algebra.}

\ssection{Examples}

\begin{expl}
  For any set $A$, $2^{A}$ is a sigma algebra.
\end{expl}

\begin{expl}
  For any set $A$,
  $\set{A, \emptyset}$ is a sigma algebra.
\end{expl}

\begin{expl}
  Let $A$ be an infinite set.
  Let $\mathcal{A}$ the collection
  of finite subsets of $A$.
  $\mathcal{A}$ is not a sigma algebra.
\end{expl}

\begin{expl}
  Let $A$ be an infinite set.
  Let $\mathcal{A}$ be the collection
  subsets of $A$ such that the set or its
  complement is finite.
  $\mathcal{A}$ is not a sigma algebra.
\end{expl}


\begin{prop}
  The intersection of a family of sigma algebras is
  a sigma algebra.
  \label{sigma_algebra:sigmaintersection}
\end{prop}

\begin{expl}
  For any infinite set $A$,
  let $\mathcal{A}$ be the set
  $$
  \Set*{
    B \subset A
  }{
    \card{B} \leq \aleph_0 \lor
    \card{C_{A}(B)} \leq \aleph_0
  }.
  $$
  $\mathcal{A}$ is an algebra;
  the
  \ct{countable/co-countable algebra}{}.
\end{expl}

\boxed{TOOD: clean up examples}
\strats
