\input{../../sheet.tex}
\sbasic
\input{../real_functions/macros.tex}
\input{../functions/macros.tex}
\input{../intervals/macros.tex}
\input{../relations/macros.tex}
\input{../set_specification/macros.tex}
\input{../real_numbers/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_extension/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../solving_equations/macros.tex}
\input{../objects/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equations/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../operations/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Differentiability}

\ssection{Why}

We want to talk about
the

\ssection{Definition}

Consider an open interval of
real numbers and a function on
the interval.
Take a real number in the interval.
It corresponds to some element in
the graph of the function.
Next take a second real number in the interval.
It too corresponds to some element in
the graph of the function.
We have two distinct elements of the
interval corresponding to two elements of the graph.

Next, consider the line in the plane which passes
through these two elements of the graph of the
function.
Consider the slope of this line, in other words,
the tangent of the angle between the line
and a horizontal line passing through the
original point.
Consider the tangent of the angle which the line
makes with the horizontal.
The quantity is the quotient
of the result on the second real number
less the result on the first real number
with the second real number less the first
real number.

For a selected first number,
define a new function which maps
a second distinct real number (in the interval)
to this quantity, the slope of the line
between them.
Next, we consider if this second function
has a limit as its argument approaches
the first fixed number.
If it does, we say that the original function is
\ct{differentiable at}{} the first number.
We call the limiting real number the
\ct{derivative at}{} the first real number of
the original function.

If the first function is differentiable at
each number in the interval of its domain,
we say that the function is \ct{differentiable}{}.
We call the function which assigns to each
real number in the interval the real number
which is the derivative at the argument of
the function the \ct{derivative of}{} the
original function.

\ssection{Notation}

Let $f: (a,b) \to \R$ and $x_0 \in (a, b)$.
Let $A = (a, b) - \set{a}$.
Let $g: A \to \R$ be such that
$g(x) = (f(x) - f(x_0))/(x - x_0)$.
We say that $f$ is differentiable at $x_0$ if
$\lim_{x \to x_0} g(x)$ exists in $\R$.
In other words, $f$ is differentiable if
\[
  \lim_{x \to x_0}
  \frac{f(x) - f(x_0)}{x - x_0}
\]
exists in $\R$.
If $f$ is differentiable at $x$ for each
$x \in (a, b)$ then $f$ is differentiable.
Let $h: (a,b) \to \R$ be such that
\[
  h(x) = \lim_{x \to x_0} \frac{f(x) - f(x_0)}{x - x_0}
\]
where $f$ is differentiable.  Then $h$ is the derivative of $f$.
\strats
