\input{../../sheet.tex}
\sbasic
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../relations/macros.tex}
\input{../functions/macros.tex}
\input{../natural_numbers/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Zero}

\ssection{Why}

If I am holding
three pebbles, and I have three
in my left hand, how many
might I have in my right hand?
None, of course!

In the notation we have developed
we find solutions of
\[
  3 + n = 3,
\]
where $n$ is a natural number.
Unfortunately, any natural number
added to three is a number different
than three.
So there is no natural number
such that this equation holds.

How can we expand our algebra
so that we can express this
new, but common, situation in
our language?

\ssection{Definition}

We consider a superset
of the natural numbers with
one additional element.
We call this new elemenet
\t{zero}
and we call this new set
the
\t{natural numbers with zero}.

\ssubsection{Extending Arithmetic}

We extend the algebra on
the natural numbers to an
algebra on the natural numbers
with zero.

We define an extension of addition,
also called
\t{addition}.
Given two natural
numbers, we define the
result as the sum.
Given a natural number
and zero,
we define the result
to be the natural number,
and vice versa,
so that addition
still commutes.
As a function, addition
by zero is the identity.

We extend multiplication.
Given two natural
numbers, we define their
product as before.
Given a natural number
and zero,
we define the product
to be the zero,
and vice versa,
so that addition
still commutes.
As a function, mutliplication
by zero is constant.

\ssubsection{A new solution}

We have extended our algebra.
We can search for solutions of:
\[
  3 + n = 3
\]
where $n$ is a natural
number or zero.
Zero is a solution (by design)!
Since no natural number
solves, zero is
the only solution.

\ssubsection{Notation}

We denote zero by $0$.
For every natural number
$n$, we defined
\[
  n + 0 = 0 + n = n \quad \text{ and } \quad n \cdot 0 = 0 \cdot n = 0
\]
\strats
