\input{../../sheet.tex}
\sbasic
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../set_specification/macros.tex}
\input{../objects/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_intersections/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../empty_set/macros.tex}
\input{../identity/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../relations/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../operations/macros.tex}
\input{../functions/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../algebras/macros.tex}
\input{../surjective_functions/macros.tex}
\input{../injective_functions/macros.tex}
\input{../function_composites/macros.tex}
\input{../groups/macros.tex}
\input{../function_inverses/macros.tex}
\input{../fields/macros.tex}
\input{../permutations/macros.tex}
\input{../vectors/macros.tex}
\input{../permutation_matrices/macros.tex}
\input{../matrix_transpose/macros.tex}
\input{../matrices/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Index Matrices}

\ssection{Why}

TODO

\ssection{Definition}

An \t{index sequence} of \t{order} $n$ is a finite sequence of distinct elements of $\upto{n}$ whose length is less than or equal to $n$.
We call the $i$th coordinate of an index sequence the \t{$i$-index} of the sequence.
The \t{index matrix} associated with an index sequence is the $r \times n$ matrix whose $i,j$th entry is 1 if the index sequences's $i$th coordinate is $j$, and $0$ otherwise.
If $r = n$ then the index matrix is a permutation matrix.

Multiplying a vector by an index matrix produces a permuted subvector.
The \t{subvector} of an $n$-vector {associated with} a length-$r$ index sequence is the product of the $r \times n$ index matrix with the $n$-dimensional vector.
Its $i$th entry is the $i$-index entry of the vector.

\ssubsection{Other Terminology}
Some authors use the term \t{index set} for index sequences; but since these are sequences (which are functions, and so relations, and so sets), they are not sets of indices, so we avoid this usage.

\ssubsection{Notation}

Let $r \leq n$ be natural numbers.
Let $\alpha: \upto{r} \to \upto{n}$ be an index sequence.
We denote the index matrix associated with $\alpha$ by $\IdxMat{\alpha}$.
This matrix $\IdxMat{\alpha}$ is an element of $\Mat{\N}{r}{n}$ and is defined by
$$
    (\IdxMat{\alpha})_{ij} = \begin{cases}
    1 & j = \alpha(i) \\
    0 & \ow
  \end{cases}
$$

Let $A$ be a nonempty set and let $x \in \Vec{A}{n}$.
then the subvector of $x$ associated with $\IdxMat{\alpha}$ (and so with $\alpha$) is
$$
  \IdxMat{\alpha}x = \pmat{x_{\alpha(1)}, \dots, x_{\alpha(r)}}
$$
We denote the product $\IdxMat{\alpha}x$ by $x_{\alpha}$.

We denote the product $\IdxMat{\alpha}X\transpose{\IdxMat{\alpha}}$ by $X_{\alpha\alpha}$.

\ssection{Multiplication}


The product of the $n \times r$ transpose of an index  matrix with an $r$ vector is the $n$ vector with
The
%
% A \t{principal submatrix} of a matrix is any matrix which can be formed by forming Multiplying an $n \times n$ matrix with an index matrix on the left and the transpose of the index matrix on the right extracts the
%
\strats
