
%!name:index_matrices
%!need:matrices
%!need:permutation_matrices
%!need:matrix_transpose

\section*{Definition}

An \t{index sequence} of \t{order} $n$ is a finite sequence of distinct elements of $\upto{n}$ whose length is less than or equal to $n$.
We call the $i$th coordinate of an index sequence the \t{$i$-index} of the sequence.
The \t{index matrix} associated with an index sequence is the $r \times n$ matrix whose $i,j$th entry is 1 if the index sequences's $i$th coordinate is $j$, and $0$ otherwise.
If $r = n$ then the index matrix is a permutation matrix.

Multiplying a vector by an index matrix produces a permuted subvector.
The \t{subvector} of an $n$-vector {associated with} a length-$r$ index sequence is the product of the $r \times  n$ index matrix with the $n$-dimensional vector.
Its $i$th entry is the $i$-index entry of the vector.

\subsection*{Other terminology}

Some authors use the term \t{index set} for index sequences; but since these are sequences (which are functions), they are not sets of indices, so we avoid this usage.

\subsection*{Notation}

Let $r \leq n$ be natural numbers.
Let $\alpha : \upto{r} \to \upto{n}$ be an index sequence.
Denote the index matrix associated with $\alpha $ by $P_\alpha $.
This matrix $P_\alpha $ is an element of $\N  ^{r \times  n}$ and is defined by
    \[
(P_a)_{ij} = \begin{cases}
1 & j = \alpha (i) \\
0 & \text{otherwise}
\end{cases}
    \]

Let $A$ be a nonempty set and let $x \in A^n$.
then the subvector of $x$ associated with $P_\alpha $ (and so with $\alpha $) is
    \[
P_\alpha  x = \pmat{x_{\alpha (1)}, \dots , x_{\alpha (r)}}
    \]
We denote the product $P_\alpha x$ by $x_{\alpha }$.
We denote the product $P_\alpha  X P_\alpha ^\top $ by $X_{\alpha \alpha }$.

%<div data-littype='section' data-litsectionlevel='1' data-litsectionnumbered='false'> Multiplication </div>
%<div data-littype='paragraph'>
%  <div data-littype='run'> </div>
%  <div data-littype='run'> The product of the $n ×r$ transpose of an index matrix
%    with an $r$ vector is the $n$ vector with </div>
%    <!--
%  <div data-littype='run'> The </div>
%  <div data-littype='run'> ❲%❳ </div>
%  <div data-littype='run'> ❲% A ❬principal submatrix❭ of a matrix is any matrix which can be formed by forming Multiplying an $n ×n$ matrix with an index matrix on the left and the transpose of the index matrix on the right extracts the❳ </div>
%  <div data-littype='run'> ❲%❳ </div>
%  <div data-littype='run'> </div>
%</div>

\blankpage