\input{../../sheet.tex}
\sbasic
\input{../intervals/macros.tex}
\input{../set_specification/macros.tex}
\input{../real_numbers/macros.tex}
\input{../set_extension/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../identity/macros.tex}
\input{../sets/macros.tex}
\input{../solving_equations/macros.tex}
\input{../objects/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equations/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../operations/macros.tex}
\input{../functions/macros.tex}
\input{../relations/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Product Sections}

\stitle{Product Sections}

\ssection{Why}

Toward a theory
of iterated integrals,
we need to generalize
rectangular strips to
arbitrary products.

\ssection{Definition}

Consider the
product of two
non-empty sets.

First, consider a subset
of this product.
For a specified element
in the first set, the
\ct{set section}{setsection}
of the subset
with respect to
that element is
the set of elements in the
second set for which
the ordered pair
of the specified element
and that element is in the subset;
the section
is a subset of the second set.
For elements of the second set,
we define sections similarly.

Second, consider a function
on the product.
For a specified element
in the first set, the
\ct{function section}{functionsection}
of the function for that
element is the function
from the second set to
the codomain of the function
which maps elements of
the second set to the result
of the function applied
to the ordered pair of
the specified element
and the element of the second set.
For elements of the second set,
we define sections similarly.

\ssubsection{Notation}

Let $X,Y$ be non-empty sets.

Let $E \subset X \cross Y$.
For $x \in X$,
we denote the section
of $E$ with respect to $x$
by $E_x$.
For $y \in Y$,
we denote the section
of $E$ with respect to $x$
by $E^y$.
For every $x \in X$ and
$y \in Y$,
\[
  E_x = \Set{y \in Y}{(x,y) \in E}
  \quad \text{ and } \quad
  E^y = \Set{x \in X}{(x,y) \in E}.
\]
$E_x \subset Y$ and $E_y \subset X$.

Let $f: X \cross Y \to Z$.
For $x \in X$,
we denote the section
of $f$ with respect to $x$
by $f_x: Y \to Z$.
For $y \in Y$,
we denote the section
of $f$ with respect to $x$
by $f^y: X \to Z$.
For every $x \in X$ and
$y \in Y$,
\[
  f_x(y) = f(x, y)
  \quad \text{ and } \quad
  f^y(z) = f(x, y).
\]
\strats
