\input{../../sheet.tex}
\sbasic
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../objects/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../sentences/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../relations/macros.tex}
\input{../families/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_equality/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../functions/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../real_sequences/macros.tex}
\input{../real_numbers/macros.tex}
\input{../function_composites/macros.tex}
\input{../direct_products/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../cardinality/macros.tex}
\input{../set_operations/macros.tex}
\input{../real_limits/macros.tex}
\input{../intervals/macros.tex}
\input{../sequences/macros.tex}
\input{../measures/macros.tex}
\input{../extended_real_numbers/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Complex Measures}

\ssection{Why}

We allow measures to take
complex values.
TODO

\ssection{Definition}

A complex-valued
function on a
sigma algebra is
\ct{countably additive}{countablyadditive}
if the result of the function applied to
the union of a disjoint countable family of
distinguished sets is the limit of the partial
sums of the results of the function applied
to each of the sets individually.
The limit of the partial sums must
exist irregardless of the summand order.

A
\ct{complex measure}{complexmeasure}
is an complex-valued
function on a
sigma algebra that is
(1) zero on the empty set and
(2) countably additive.
We call the result of the function
applied to a set in the sigma
algebra the
\ct{complex measure}{signedmeasure}
(or when no ambiguity arises, the
\ct{measure}{})
of the set.

Since the codomain of
a complex measures is
the complex numbers,
the sum corresponding
to every countable union
must be absolutely convergent (?)
(TODO: define).

\ssubsection{Notation}

We denote complex measures by $\mu$
a mnemonic for \say{measure.}
Let $C$ denote the set
of complex numbers.
Let
$(X, \mathcal{A})$
be a measurable space
and let
$\mu: \mathcal{A} \to C$.
Then $\mu$ is a complex measure if
\begin{enumerate}
  \item $\mu(\emptyset) = 0$ and
  \item
  $\mu(\union_{i} A_i) =
    \lim_{n \to \infty}
      \sum_{k = 1}^{n} \mu(A_k)$
  for all disjoint families $\seq{A}$.
\end{enumerate}
\strats
