
%!name:decisions
%!need:set_numbers
%!need:uncertain_outcomes
%!need:orders

\section*{Why}

We want to discuss making a decision.\footnote{Future editions will expand.}
To discuss decisions, we first must speak of the choices to be made.

\section*{Definition}

We have a set which includes all possible choices.
The set is called the \t{actions}, \t{acts}, \t{decisions}, \t{choices} or \t{designs}.

For each decision, we have a set which includes all possible outcomes.
Often the outcomes are uncertain, and associated with the future (see \sheetref{uncertain_outcomes}{Uncertain Outcomes}).

Since we select an action prior to observing the outcome, we want to talk about which actions and outcomes are preferable to others.
We call an action-outcome pair a \t{history}.
We refer to the set of action-outcome pairs the \t{histories}.
A \t{preference} is an order on histories.

A \t{simple decision problem} is a triple $(A, \set{O_a}_{a \in A}, \preceq)$ in which $A$ is a set of actions, $\set{O_a}$ is a family of sets of outcomes, and $\preceq$ is a preference on the histories $\Set*{(a, o)}{a \in A, o \in O_a}$.

\section*{Example: party}

Consider deciding whether to host a party indoors or outdoors.
We are unsure of the weather.
We have a set of two actions $A = \set{\textsc{In}, \textsc{Out}}$ and a set of two outcomes (the same for each action) $O_a = W = \set{\textsc{Rain}, \textsc{Shine}}$ for $a \in A$.
Although many orders on $A \times  W$ exist, one such order is
    \[
(\textsc{Out}, \textsc{Shine}) \prec (\textsc{In}, \textsc{Rain}) \prec (\textsc{In}, \textsc{Shine}) \prec (\textsc{Out}, \textsc{Rain}).
    \]
In other words, having the party outside in the sun is preferred to having it inside when it is raining, but both of these are preferred to having it inside when the sun is shining, and all of these are preferred to having it outdoors in the rain.

\section*{Best actions}

Let $(A, \set{O_a}, \preceq)$ be a simple decision problem in which $O_a = S$ for each $a \in A$.
Let $o \in S$.
An action $a \in A$ is \t{best for outcome $o$} if $(a, o) \preceq (a', o)$ for all $a' \in A$.
An action $a \in A$ is \t{best for all outcomes} (or \t{uniformly best}) if, for all $o \in O$, $(a, o) \preceq (a', o')$ for all $a' \in A, b' \in O$.\footnote{Future editions will clarify, and may remove this section.}

In the party example, the best action for $\textsc{Rain}$ is $\textsc{In}$ and the best action for $\textsc{Shine}$ is \textsc{Out}.
On the other hand, there is no uniformly best action.
For the action $\textsc{Out}$, there is an outcome $\textsc{Rain}$, and action-outcome pair $(\textsc{In}, \textsc{Rain})$ so that $(\textsc{In}, \textsc{Rain}) \prec (\textsc{Out}, \textsc{Rain})$.
In other words, $\textsc{Out}$ is not uniformly best, because there is an outcome, $\textsc{Rain}$ for which the action $\textsc{In}$ is preferred.
Similarly for $\textsc{In}$.
