
%!name:consistent_inductors
%!need:predictors

\section*{Why}

We discuss inductors that produce relations consistent with their given datasets.

\section*{Definition}

Let $(x_1, y_1), \dots , (x_n, y_n)$ be a dataset in $X \times  Y$.
Let $\mathcal{R} $ be the set of all relations on $X \times Y$.

A \t{consistent inductor} $\set{G_n: (X \times  Y)^n \to \mathcal{R} }_{n}$ is one for which, for all $n \in \N  $, for all $D_n \in (X \times  Y)^n$, $D$ is consistent with $G_n(D_n)$.
In other words, a consistent inductor always produces a relation with which the dataset is consistent.

The interpretation follows.
Fix a relation $R^\star$.
And let every dataset ``shown'' to the algorithm $G_n$ be constructed by selecting elements from $R^{\star}$.
In other words, every dataset is a sequence in $R^\star$.
In this case, a dataset $D_n \in (X \times  Y)^n$ is always consistent with $R^\star$ and so a consistent inductor will never ``eliminate'' $R^{\star}$.
In other words, the inductor, in order to be consistent ``must eliminate'' every inconsistent relation.

We may ``hope'' to give the algorithm a ``large and diverse'' datset, so that several of the elements of $R^\star$ are included.
In this case, the algorithm can ``eliminate'' many smaller relations in $\mathcal{R} $ which did not include records in the dataset.

\section*{Functionally consistent}

The rub is that any dataset is consistent with the complete relation $X \times  Y$.
So we can often consider a set $\mathcal{H}  \subset \mathcal{R} $ of relations.
It is common to call this a \t{hypothesis class}, especially for the case in which it consists of functional relations.
