%!name:statements
%!need:objects

\s{Why}

We want to succinctly and unambiguously record statements about names and the objects and sets of objects which the names refer to.

\s{Definition}

So far we have three kinds of sentences which we would like to record.

\begin{enumerate}

  \item
  \textbf{Names}
  We want to declare that we are using a particular name.
  When we start with a blank slate, once we have declared a name we do not use the same name twice.
  So we will want to keep track of which names are in use.

  \item
  \textbf{Identities}
  We want to declare that two names are equal.
  When we have names, we want to say when the identities of those names are the same.

  \item
  \textbf{Belongings}
  We want to declare when the object represented by one name is an element of the set represented by a second name.

\end{enumerate}

Our main purpose is to keep a list of the statements we have made.
Experience suggests that we start with an example.

Suppose we want to summarize the following english language description of some names and objects.
Denote an object by $a$.
Denote the same object by $a'$
In other words, $a$ equals $a'$.
Denote a set by $A$.
The object denoted by $a$ is an element of the set denoted by $A$.

\begin{account}[Example]
\name{$a$}
\name{$a'$}
\have{}{$a = a'$}
\name{$A$}
\have{}{$a \in A'$}
\end{account}

We have three primary

In the English language we have nouns and verbs.
The nouns reference objects and the verbs reflect the relations of these objects to each other.
In these sheets the nouns are names (introduced in \sheetref{}{Objects}) and we speak only in the present tense.
We use only the verbs \say{is} and \say{belongs}.

We say that these two verbs put two objects

There
There will only be two verbs and they are.
There are only two verbs: equals
We speak only in the present testand we have \t{relational symbols}.
A \t{terminal} is a relational symbol, a left object and a right object.
We will only make use of relational symb

For now, denote a relational symbol by \fbox{$s$}.
Denote a name by \fbox{$a$}
