\input{../../sheet.tex}
\sbasic
\input{../objects/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../sentences/macros.tex}
\input{../set_equality/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../relations/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../functions/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_operations/macros.tex}
\input{../injective_functions/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../cardinality/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../sigma_algebras/macros.tex}
\input{../direct_products/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Product Sigma Algebras}

\ssection{Why}

We want to generalize the
construction of cover area
as generated as a product
of two cover lengths, and more
generally for arbitrary
measure spaces.
TODO

\ssection{Definition}

Consider two measurable spaces.
The \ct{product base set}{} is
the cartesian product of
the first base set with
the second base set.
A first distinguished set
is a distinguished set
of the first measurable space,
and likewise for a second distinguished set.

A
\ct{rectangle
with measurable sides}
{rectanglewithmeasurablesides}
is a set in product base set
which is
a product of a first
distinguished set with a second
distinguished set.
The
\ct{product sigma
algebra}
{product sigma algebra}
is the sigma algebra
generated by the rectangles
with measurable sides.

The \ct{product measurable space}{}
is the measurable space
whose base set is the product
base set and whose sigma algebra
is the product sigma algebra.

\ssubsection{Notation}
Let
$(X, \SA)$ and $(Y, \SB)$
be measurable spaces.
The product base set is
$X \cross Y$.
A set
$R \in X \cross Y$
is a rectangle with measurable
sides if $R = A \cross B$ for
$A \in \SA$ and $B \in \SB$.
We denote the product sigma algebra
of $\SA$ and $\SB$ by $\SA \cross \SB$.
$(X \cross Y, \SA \cross \SB)$ is
the product measurable space.
\strats
