\input{../../sheet.tex}
\sbasic
\input{../intervals/macros.tex}
\input{../set_operations/macros.tex}
\input{../real_numbers/macros.tex}
\input{../algebras/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../operations/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../functions/macros.tex}
\input{../solving_equations/macros.tex}
\input{../relations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equations/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../objects/macros.tex}
\input{../sets/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Convex Sets}

\ssection{Why}

We speak of sets of
real numbers which are
like intervals.

\ssection{Definition}

A
\ct{convex combination}{convexcombination}
of two distinct real numbers
is an element of the closed interval they
delimit.
A
\ct{convex set}{convexset}
of real numbers
contains each convex combination
of any two of its elements.

The \ct{length}{}
of a convex
combination
is the real
number in $[0,1]$
which is
the ratio of
the combination
less the lower
endpoint
to the
upper endpoint
less the lower
endpoint.

\ssubsection{Notation}

Denote the real numbers
by $R$.
Let $A \subset R$ be convex.
Then
for all $a, b \in A$,
$[a, b] \subset A$.

Suppose $A$ contains
at least two element.
Let $a, b \in A$
with $a < b$.
If $c$ is the combination
of $a$ and $b$, then
the length of $c$
is $(c-a)/(b-a)$.

If $A$ is convex,
then for each
$a, b \in A$,
and $\theta \in [0, 1]$,
\[
  \theta a + (1-\theta) b \in A.
\]

\ssection{Examples}

\begin{expl}
  The real numbers
  are a convex set.
\end{expl}

\begin{expl}
  Real intervals are convex.
\end{expl}

\begin{expl}
  Let $a,b$ be
  non-equal real numbers.
  The set $\set{a,b}$ is
  not convex.
\end{expl}

\begin{expl}
  The empty set is convex
\end{expl}

\begin{expl}
  Let $a$ be a real number.
  The set $\set{a}$ is convex.
\end{expl}

\begin{expl}
  Let $[a, b]$
  and $[c,d]$ be
  two disjoint real
  intervals.
  The set
  $[a,b]\union[c,d]$
  is not convex.
\end{expl}
\strats
