%!name:eigenvalues_and_eigenvectors
%!need:real_matrices
%!need:real_vectors
%!need:norms
%!need:matrix_determinants
%!need:monic_polynomials

\section*{Why}

We discuss vectors for which the action of a matrix is scalar multiplication.
  \ifhmode\unskip\fi\footnote{
Future editions will expand.
  }

\section*{Definition}

Let $A \in \R ^{n \times n}$ be a square matrix.
A nonzero vector $x \in \R ^{n}$ is an \t{eigenvector} of $A$, and $\lambda  \in \R $ is its corresponding \t{eigenvalue}, if $A x = \lambda  x$.
In other words, $x \neq 0$ is an eigenvector if the action of $A$ on $x$ is to mimic scalar multiplication.

Speaking of eigenvalues is sensible only when the matrix involved is square.
In other words, when the domain and codomain are the same.
We often care about eigenvalue computations when a matrix is compounded iteratively.


%<div data-littype='paragraph'>
%  <div data-littype='run'> ❲%\ssubsection{Notation}❳ </div>
%  <div data-littype='run'> ❲%❳ </div>
%  <div data-littype='run'> ❲%The spectrum of $A ∈ 𝗥^{n × n}$ is sometimes denoted $\Lambda(A)$.❳ </div>
%</div>

\section*{Eigenspaces}

If $x$ is an eigenvector with eigenvalue $\lambda $, then for any $\alpha  \in \R $, $\alpha  x$ is an eigenvector with eigenvalue $\alpha \lambda $, since $A (\alpha  x) = \alpha  (Ax) = (\alpha \lambda ) x$.
In other words, if $A$ has an eigenvector then the action of $A$ on some subspace $S \subset \R ^n$ is to mimic scalar multiplication.
In this case, we call the subspace $S$ an \t{eigenspace}, and any nonzero $x \in S$ an eigenvector.

An eigenspace is an \t{invariant subspace} of $A$.
In other words, if $E$ is an eigenspace corresponding to eigenvalue $\lambda $ then $AE \subset E$.

The dimension of $E$ is the maximum number of linear independent eigenvectors which have the same eigenvalue $\lambda $.
We call this number the \t{geometric multiplicity} of $\lambda $.

\section*{Characteristic polynomial}

If $x$ is an eigenvector for $A$ associated with $\lambda $ then $Ax = \lambda  x$ so $Ax - \lambda  x = 0$ and $(A - \lambda  I)x = 0$.
In other words, $x$ is an element of the nullspace of $A - \lambda  I$. Or equivalently, $\lambda  I - A$.

The \t{characteristic polynomial} of $A \in \R ^{n \times n}$ is the polynomial $p: \R  \to \R $ in defined by
  \[
p(x) = \det (zI - A).
  \]
$p$ is monic: the coefficient of the degree $n$ term is 1.
\begin{proposition}
$\lambda $ is an eigenvalue of $A$ if and only if $p(\lambda ) = 0$.
\begin{proof}
Since $\lambda $ is an eigenvalue if and only if there is a nonzero vector $x$ such that $\lambda  x - Ax = 0$, if and only if $\lambda  I - A$ is singular, if and only if $\det(\lambda  I - A) = 0$.
\end{proof}
\label{proposition:eigenvalues_and_eigenvectors:characteristic_polynomial}
\end{proposition}
A simple consequence of Proposition~\ref{proposition:eigenvalues_and_eigenvectors:characteristic_polynomial} is that a (real) matrix may have complex eigenvalues.


%formerly Matrix Eigenvectors sheet
%%!name:matrix_eigenvectors
%%!need:matrix-vector_products
%%!need:norms
%\ssection{Why}\footnote{Future editions will include an account.}
%\ssection{Definition}
%If the result of multiplying a vector by a real square matrix is the same as scaling the vector by a real number then we call the vector a \t{scaled vector}.
%If a vector is a scaled vector, then the result of scaling it with any real number is a scaled vector.
%% ($Ax = \alpha x \implies A \beta x = \beta Ax = \beta \alpha x$).
%The scaled version of a scaled vector is acted upon by the matrix in a similar manner as the original scaled vector.
%So we want to characterize this notion by picking one representative member from this set of vectors which are scalar multiples of each other, and a reasonable choice is the vector which has norm one.\footnote{Future editions will change this language.}
%An \t{eigenvector} is a scaled vector whose norm is one.
%An \t{eigenvalue} corresponding to an eigenvector is the real number by which the eigenvector is scaled by the matrix.
%So eigenvectors and eigenvalues come in pairs.
%\blankpage
