%!name:metrics
%%!need:real_numbers
%!need:distance
%!need:absolute_value
%!refs:bert_mendelson/introduction_to_topology/metric_spaces/introduction
%!refs:bert_mendelson/introduction_to_topology/metric_spaces/metric_spaces

\ssection{Why}

We want to talk about a set with a prescribed quantitative degree of closeness (or distance) between its elements.

\ssection{Definition}

The correspondences
which serve as a
degree of closeness,
or measure of distance, must
satisfy our previously developed (see \sheetref{distance}{Distance}) notion of distance.

A function on ordered pairs which does not depend on the order of the elements so considered is \t{symmetric}.
A function into the real numbers which takes only nonnegative values is \t{nonnegative}.
A repeated pair is an ordered pair of the same element twice.
A function which satisfies a triangle inequality for any three elements is \t{triangularly transitive}.

A \t{metric} (or \t{distance function}) is a function on ordered pairs of elements of a set which is symmetric, non-negative, zero only on repeated pairs, and triangularly transitive.
A \t{metric space} is an ordered pair whose first coordinate is a nonempty set and whose second coordinate is a metric.

In a metric space, we say that one pair of objects is \t{closer} together if the metric of the first pair is smaller than the metric value of the second pair.

Notice that a set can be made into different metric spaces by using different metrics.

\ssubsection{Notation}

Let $A$ be a set.
We commonly denote a metric by the letter $d$, as a mnemonic for \say{distance.}
Let $d: A \times A \to \R$.
Then $d$ is a metric if:
\begin{enumerate}
  \item
    it is non-negative,
    which we tend to denote by
    $$
      d(a, b) \geq 0, \quad \forall a,b \in A.
    $$
    %We read this notation as:
    %\say{the distance between
    %a and b is at least zero}
  \item
    it is $0$ only on repeated pairs, which we tend to denote
    by
    $$
      d(a, b) = 0 \iff a = b, \quad \forall a,b \in A.
    $$

%    We read this notation as:
%    \say{the distance between
%    two objects is zero
%    a and b is at least zero}
  \item
    it is symmetric, which we tend to denote by:
    $$
      d(a, b) = d(b, a), \quad \forall a,b \in A.
    $$
  \item
    it is triangularly transitive, which we tend to
    denote by
    $$
      d(a, b) \leq d(a, c) + d(c, b), \quad \forall a,b,c \in A.
    $$
\end{enumerate}
As usual, we denote the metric space
of $A$ with $d$ by
$(A, d)$.

\ssection{Examples}

$\R$ with the absolute value distance is a metric space. As is $\R^2$ and $\R^3$ with the Euclidean distance. $\R^n$ with Euclidean metric is an example of a metric space for which the objects ($n$-dimensional tuples of real numbers) are impossible to visualize.
