\input{../../sheet.tex}
\sbasic
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../real_numbers/macros.tex}
\input{../intervals/macros.tex}
\input{../real_functions/macros.tex}
\input{../objects/macros.tex}
\input{../sentences/macros.tex}
\input{../partitions/macros.tex}
\input{../characteristic_functions/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../set_complements/macros.tex}
\input{../operations/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../set_specification/macros.tex}
\input{../relations/macros.tex}
\input{../simple_functions/macros.tex}
\input{../measurable_functions/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../algebras/macros.tex}
\input{../set_equality/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_intersections/macros.tex}
\input{../empty_set/macros.tex}
\input{../functions/macros.tex}
\input{../simple_integrals/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_operations/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../nonnegative_integrals/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../cardinality/macros.tex}
\input{../real_integrals/macros.tex}
\input{../measures/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Exchangeable Measures}

\ssection{Why}

We want to compute integrals
with respect to arbitrary measures.
If we find a special measure
with which we can compute integrals,
would there
be some way to translate
integrals against another measure
into integrals against this special
measure?

It would suffice to produce a special function
whose integral against the base measure
would over any measurable set gave
the measure of the set under the alternate
measure.
In this case, the monotone convergence
theorem would say that the integral of
any function under the alternate
measure was the integral of the function
against the special function under the
base measure.

No small miracle is that the condition
for this exchange is extremely simple.
In this sheet, we will define the
condition. In a later sheet we will
construct the special function.

\ssection{Definition}

Consider two measures.
Suppose there exists
a measurable set for which the first
was positive but the second was zero.
Then we have no hope of exchanging
these measures, because the integral
of any function over this set against
the second measure is zero.

So let us rule out this case.
Suppose that whenever the
first was positive on a set,
the second was positive on that set.
The contrapositive is that
whenever the second is zero
on a set, the first is zero on the same.
This condition
is sufficient for exchangeability.

A first measure is \ct{exchangeable}{}
with respect to a second measure
if the first measure of any measurable
set is zero whenever the second measure
of that set is zero.
As we said earlier, this condition
means that the first measure
is never nonzero on a set for which
the second measure is zero.
In this case, we also say that
the first measure is
\ct{absolutely continuous}{}
with respect to the second measure.

\ssubsection{Notation}

Let $(X, \SA)$ be a measurable space.
Let $\mu$ and $\nu$ be two measures
on $\SA$.
Then $\nu$ is exchangeable with $\mu$
if for all measurable $A \in \SA$
\[
  \mu(A) = 0 \implies \nu(A) = 0.
\]
Equivalently,
\[
  \nu(A) > 0 \implies \mu(A) = 0
\]
for all $A \in \SA$.
\strats
