
%!name:introduction

The Bourbaki Project is a collection of documents describing mathematical concepts, terms, results and notation.

%% Each is named and labeled with prerequisites.
%% The prerequisites are the names of those documents which should be first read by the unaquainted reader.

\section*{Sheets}

We call these documents \t{sheets}.
They are only ever two-pages long and sometimes shorter.
They can be printed on a single sheet of paper, hence the name sheet.
In a book, they occupy two facing pages.
The decision to cap at two pages is arbitrary.
But our experience suggests it is convenient.

\section*{Prerequisites}

Each sheet is labeled with the names of those sheets which are its immediate prerequisites, with the names of those sheets for which it is an immediate prerequisite, and a diagram illustrating the dependencies between all its prerequisites.

For example, the sheet \sheetref{relations}{Relations}needs the sheet \sheetref{ordered_pairs}{Ordered Pairs}.
The reason, in this case, is that the concept of a relation is discussed using the concept of an ordered pair of objects.
And since the phrase \say{ordered pair of objects} makes sense only if we know what is meant by object (discussed in the sheet \sheetref{objects}{Objects}), the sheet \sheetref{relations}{Relations}needs the sheet \sheetref{objects}{Objects} also.
The reader unacquainted with ordered pairs and objects must read (at least) these two sheets before the sheet on relations.
In this case (and in every case) the prerequisites are naturally ordered.
 \sheetref{objects}{Objects}ought to be read first, before \sheetref{ordered_pairs}{Ordered Pairs}, before \sheetref{relations}{Relations}.
Such an ordering always exists because we ensure that if a sheet $X$ needs a sheet $Y$, then $Y$ can not need $X$ or any sheet that needs $X$.
A sheet is an immediate prerequisite if it is not prerequisite to any other prerequisite.

%% For convenience, we list only the immediate prerequisitesfor each sheet only those prerequisite sheets which are not a prerequisite to another prerequisite.
%% So if \sheetref{ordered_pairs}{Ordered Pairs} needs \sheetref{objects}{Objects}, then even though \sheetref{relations}{Relations} needs both \sheetref{ordered_pairs}{Ordered Pairs} and \sheetref{objects}{Objects}, we would only list \sheetref{ordered_pairs}{Ordered Pairs}.
%% a page are minimal. That is to say,
%% for sheet $X$ we only list the sheets
%% which are in the needs of $X$
%% and not needed by any other sheet
%% in the needs of $X$.
%% If $X$, $Y$ and $Z$ are as before,
%% then we only list $Y$ as $X$'s needs
%% because $Z$ is implicit (through $Y$).
%% The sheets and their needs are probably
%% best explored by browsing the project;
%% the index is
%% a reasonable starting point.

\section*{Preface}

The project is like a map.
The landmarks are sheets, or really concepts.
Walking is reading.
And you must walk along the trails specified by the prerequisites.

\subsection*{Aims}

Our primary aim is two-fold.
First, to provide useful exposition to teach the concepts to an unacquainted reader (here the prerequisites help).
And second, to serve as a reference for further work.
It is a welcomed concomitant that we better understand and develop the mathematical concepts ourselves.

\subsection*{Caveats}

There are two caveats.
First, we give only one path to concepts.
The point is that our way of structuring the concepts (and hence the prerequisites) is just one way, and there are many ways, since there are equivalent concepts, alternate proofs, and so on.
The second caveat is a wink.
These sheets are fiction.
They contain only ideas.
We have done our best to eliminate all false statements.
The game for the practical cogitator is to fit these puzzle pieces to reality.
%% In this edition, very little is said about fitting these puzzle pieces to reality.
%% But very little is said about fitting these puzzle pieces to reality.
%%\vfill
%%\begin{center}{\small The project is supported by
%%funds from the Department of
%%Defense of the United States of America
%%and Stanford University.}\end{center}
