\input{../../sheet.tex}
\sbasic
\input{../unordered_pairs/macros.tex}
\input{../empty_set/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../surjective_functions/macros.tex}
\input{../injective_functions/macros.tex}
\input{../function_composites/macros.tex}
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../relations/macros.tex}
\input{../function_inverses/macros.tex}
\input{../equivalence_relations/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../power_set/macros.tex}
\input{../functions/macros.tex}
\input{../equivalent_sets/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../natural_addition/macros.tex}
\input{../finite_sets/macros.tex}
\input{../set_specification/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../natural_difference/macros.tex}
\input{../undirected_graphs/macros.tex}
\input{../set_unions/macros.tex}
\input{../direct_products/macros.tex}
\input{../graph_paths/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Chordal Graphs}

\ssection{Why}

A \t{chord} for a path in an undirected graph is an edge between two non-consecutive vertices of the path; similarly for a cycle.
We think of a chord as a one-edge shortcut between two vertices of a path.
If a path has a chord, it can be reduced to a shorter path.
So a shortest path between two vertices is chordless.
The converse, however, is not true: a chordless path is not necessarily a shortest path.

An undirected graph is \t{chordal} if every cycle of length greather than three has a chord.
Using this property, to every cycle in a chordal graph there corresponds at least one cycle of length three.
Chordal graphs are also called \t{rigid-circuit graphs}, \t{triangulated graphs}, \t{perfect elimination graphs}, \t{decomposable graphs}, and \t{acyclic graphs}.
But we will only ever call them chordal graphs.

A \t{cactus graph} is an undirected graph with no cycles of length greater than three.
Both trees and forests are cactus graphs.
All cactus graphs are trivially chordal.


\ssubsection{Notation}

Let $G = (V, E)$ be an undirected graph.
A chord in a path $(v_0, v_1, \dots, v_k)$ of $G$ is an edge $\set{v_i, v_j}$ with $\abs{j - i} > 1$.
A chord in a cycle $(v_0, v_1, \dots, v_{k-1}, v_0)$ of $G$ is an edge $\set{v_i, v_j}$ with $(j - i) \mod k > 1$.

\ssection{Examples}

Trees and forests (and any cactus graph) are trivially chordal.
Additionally:

\begin{prop}
  Complete graphs are chordal.
\end{prop}

\ssection{Properties}

\begin{prop}
  Any subgraph of a chordal graph is chordal.

  \begin{proof}
    A consequence of the definition, since every cycle of the subgraph is a cycle of the original graph, and so also with the chords.
  \end{proof}
\end{prop}
\strats
