\input{../../sheet.tex}
\sbasic
\input{../objects/macros.tex}
\input{../identity/macros.tex}
\input{../sets/macros.tex}
\input{../set_equality/macros.tex}
\input{../sentences/macros.tex}
\input{../relations/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../empty_set/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../functions/macros.tex}
\input{../power_set/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_operations/macros.tex}
\input{../cardinality/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Subset Algebras}

\ssection{Why}

We speak of a subset system with set-algebraic properties.

\ssection{Definition}

A \t{subset algebra}
is a subset system for which
(1) the base set is distinguished
(2) the complement of a distinguished
set is distinguished
(3) the union of two distinguished sets
is distinguished.

We call the set of distinguished sets
an \t{algebra} on the the base set.
We justify this
language by showing that the standard set
operations applied to distinguished sets
result in distinguished sets.

If a set of subsets is closed under complements
it contains the base set
if and only if
it contains the empty set.
So we can replace condition (1) by insisting
that the algebra contain the empty set.
Similarly, if a non-empty set of subsets
is closed under complements and unions
then it contains the base set: the union
of a distinguished set and its complement.
Thus we can replace condition (1) by insisting
that the algebra be non-empty.

\ssubsection{Notation}

The notation follows that of a subset system.
Let $(A, \mathcal{A})$ be a subset algebra.
We also say \say{let $\mathcal{A}$ be
an algebra on $A$.}
Moreover, since the largest element of the
algebra is the base set, we can say without
ambiguity: \say{let $\mathcal{A}$ be an algebra.}

\ssection{Properties}

\begin{prop}
  For any subset algebra, $\emptyset$ is distinguished.
\end{prop}

\begin{prop}
  For any subset algebra,
  for any distinguished sets,
  (a) the intersection is distinguished and
  (b) their symmetric difference is distinguished.
  So, if one contains the other, the complement
  of the smaller in the larger is distinguished.
\end{prop}

\begin{prop}
  For any subset algebra,
  for any finite family of distinguished sets,
  (a) the finite family union and
  (b) the finite family intersection
  are both distinguished.
\end{prop}

So we could have defined an algebra
by insisting it be closed under finite
intersections.

\ssection{Examples}

\begin{expl}
  For any set $A$, $(A, 2^{A})$ is a subset algebra.
\end{expl}

\begin{expl}
  For any set $A$, $(A, \set{A, \emptyset})$ is a subset algebra.
\end{expl}

\begin{expl}
  For any infinite set $A$,
  let $\mathcal{A}$ be the set
  $$
  \Set*{
    B \subset A
  }{
    \card{B} < \aleph_0 \lor
    \card{C_{A}(B)} < \aleph_0
  }.
  $$
  $\mathcal{A}$ is an algebra;
  the
  \t{finite/co-finite algebra}.
\end{expl}

\begin{expl}
  For any infinite set $A$,
  let $\mathcal{A}$ be the set
  $$
  \Set*{
    B \subset A
  }{
    \card{B} \leq \aleph_0 \lor
    \card{C_{A}(B)} \leq \aleph_0
  }.
  $$
  $\mathcal{A}$ is an algebra;
  the
  \t{countable/co-countable algebra}.
\end{expl}


\begin{expl}
  For any infinite set $A$,
  let $\mathcal{A}$ be the set
  $$
  \Set*{
    B \subset A
  }{
    \card{B} \leq \aleph_0
  }.
  $$
  $\mathcal{A}$ is not an algebra.
\end{expl}

\begin{expl}
  Let $A$ be an uncountable set.
  Let $\mathcal{A}$ be the collection
  of all countable subsets of $A$.
  $\mathcal{A}$ is not a sigma algebra.
\end{expl}
\strats
