\input{../../sheet.tex}
\sbasic
\input{../families/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../solving_equations/macros.tex}
\input{../objects/macros.tex}
\input{../relations/macros.tex}
\input{../function_composition/macros.tex}
\input{../direct_products/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../sentences/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../functions/macros.tex}
\input{../operations/macros.tex}
\input{../sequences/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_specification/macros.tex}
\input{../set_equality/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../algebras/macros.tex}
\input{../real_sequences/macros.tex}
\input{../real_numbers/macros.tex}
\input{../subset_systems/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../cardinality/macros.tex}
\input{../set_operations/macros.tex}
\input{../real_limits/macros.tex}
\input{../intervals/macros.tex}
\input{../measures/macros.tex}
\input{../extended_real_numbers/macros.tex}
\input{../signed_measures/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Signed Measure Examples}

\ssection{Why}

Let us consider
examples of signed measures.
TODO

\ssection{Examples}

Consider an integrable
function defined on
some measurable space.
The extended-real-valued
funciton which assigns to
each distinguished set the
value of the integrating
the function over that set
is a signed measure. See
Example~\ref{expl:signedintegral}.

Consider

\begin{expl}
  \label{expl:signedintegral}
  Let $(X, \SA, \mu)$
  a measure space.
  Let $R$ denote the
  set of real numbers.
  Let $f: X \to R$ an integrable
  function.
  Define $\nu: \SA \to R$ by
  \[
    \nu(A) = \int_{A} f d\mu.
  \]
  Then $\nu$ is a signed measure.
  \begin{proof}
    First,
    \[
      \nu(\emptyset) = \int f\chi_{\emptyset} d\mu = \int 0 d\mu = 0.
    \]
    Next, let $\seq{A}$ disjoint.
    Notice that,
    \[
      \chi_{\union_{i = 1}^{n} A_k} = \sum_{i = k}^{n} \chi_{A_k}
    \]
    so for all $n$,
  \end{proof}
\end{expl}
\strats
