\input{../../sheet.tex}
\sbasic
\input{../sets/macros.tex}
\input{../objects/macros.tex}
\input{../set_equality/macros.tex}
\input{../sentences/macros.tex}
\input{../identity/macros.tex}
\input{../operations/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_specification/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../relations/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../functions/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../function_composition/macros.tex}
\input{../direct_products/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../sequences/macros.tex}
\input{../real_numbers/macros.tex}
\input{../length/macros.tex}
\input{../real_sequences/macros.tex}
\input{../absolute_value/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Real Convergence}

\ssection{Why}

We want to talk about
sequences of real numbers
which, as we go further
and further in the sequence,
get closer and closer to
some fixed real number.
Not all sequences have this
property, but many do.

\ssection{Definition}

Consider a sequence of real
numbers.
If the sequence is going to
end up somewhere in the real
numbers, we need to know where.
Consider a real number.
Suppose that for any positive
real number, no matter how small,
there exists a natural number so that
the any term corresponding to a natural
number larger than the first natural number
is no more different than that positive number
from the real number considered.

In this case, we call the real number
a \ct{limit}{} of the sequence. We say
that the sequence \ct{converges}{} to
that real number.
Not all sequences \ct{converge}{}.

\ssection{Notation}

Let $x: \N \to \R$ be a sequence of
real numbers.
Let $y \in \R$.

First,
suppose that
for each $\epsilon > 0$
there exists an $n_\epsilon \in \N$ so that
$\abs{x_n - y} < \epsilon$
for each $n \geq n_\epsilon$.
In this case, $x$ converges to $y$.
The real number
$y$ is the limit
of
the sequence $x$.

Second, suppose that there exists
an $\epsilon > 0$ so that
for each $n \in N$, there
exists $m_n \geq n$ so that
$\abs{x_{m_n} - y} > \epsilon$
for each $y \in \R$.
In this case $x$ does not converge.
\strats
