%!name:affine_sets
%!need:n-dimensional_space
%!need:n-dimensional_lines
%!refs:rockafeller/section_1/affine_sets

\section*{Definition}

A subset of $\R ^n$ is \t{affine} (or an \t{affine variety}, \t{linear variety}, or \t{flat}) if it contains the lines through each of its points.

Some authors use the term \t{affine subspace}, but we avoid this terminology because affine sets are not subspaces.
In fact, they are translated subspaces.

\subsection*{Examples}

The empty set is trivially an affine set.
The entire set of points in $n$-dimensional space is an affine set.
Any singleton is an affine set.

Our definition is meant to capture the intuitive idea of an infinite, uncurved set, like a line or a plane in space.

\subsection*{Notation}

As usual, let $L(x, y)$ denote the line between $x, y \in \R ^n$.
The set $M \subset \R ^n$ is affine if $L(a, b) \subset M$ for all $a, b \in M$.
For any $x, y \in M$ and $\lambda  \in \R $,
  \[
(1-\lambda )x + \lambda y \in M.
  \]

\section*{Translations}

The set of affine sets is closed under translation.
\begin{proposition}Let $M \subset \R ^n$ affine.
Then $M + a$ is affine for any $a \in \R $.
\begin{proof}Suppose $x, y \in M+a$.
There exist $\tilde{x}, \tilde{y} \in M$ with $x = \tilde{x} + a$ and $y = \tilde{y} + a$.
For any $\lambda  \in \R $,
    \[
\begin{aligned}
(1-\lambda )x + \lambda y & = (1-\lambda )(\tilde{x} + a) + \lambda (\tilde{y} + a) \\
&= ((1-\lambda )\tilde{x} + \lambda \tilde{y}) + a.
\end{aligned}
    \]\end{proof}\end{proposition}

An affine set $M$ is \t{parallel} to an affine set $L$ if there exists $a \in \R ^n$ so that $M = L + a$.
The relation "$M$ is parallel to $L$" on the set of affine sets is an equivalence relation.
This notion of parallelism is more restrictive than the natural one, in which we may speak of a line being parallel to a plane.
We must speak of a line which is parallel to another line within the given plane.

\section*{Properties}

The set of affine sets is closed under intersection.
\begin{proposition}If $\mathcal{M} $ is a family of affine sets, then $\cap \mathcal{M} $ is affine.\end{proposition}
