\input{../../sheet.tex}
\sbasic
\input{../sentences/macros.tex}
\input{../objects/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../empty_set/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../relations/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../set_equality/macros.tex}
\input{../functions/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_operations/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../cardinality/macros.tex}
\input{../measures/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Finite Measures}

\ssection{Why}

Sometimes we want finite measures.
TODO: which times?

\ssection{Definition}

A measurable set is
\ct{finite}{setfinite}
if its measure is a real number.
The measure space itself is
\ct{finite}{spacefinite}
if the base set is finite.

A measurable set is
\ct{sigma-finite}{setsigmafinite}
if there exists a sequence of
finite measurable sets whose
union is the set.
The measure space itself is
\ct{sigma-finite}{spacesigmafinite}
if the base set is sigma finite.

\ssubsection{Notation}

We denote that a measure
space is finite by saying
\say{Let $(A, \mathcal{A}, \mu)$
and $\mu(A) < +\infty$.}

\begin{expl}
Let $(A, \mathcal{A})$ be a measurable space.

The counting measure on $(A, \mathcal{A})$ is
finite if and only if the base set is finite.
It is sigma finite if and only if the base
set is a union of a sequence of finite sets.

If $\mathcal{A} = 2^A$, then the counting
measure is sigma finite if and only if
$A$ is countable.
\end{expl}

\begin{expl}
A point mass measure is finite.
\end{expl}

\begin{expl}
Let $R$ be the set of real numbers.
The Lebesgue measure on
$(R, \mathcal{B}(R))$ is sigma finite.
\end{expl}
\strats
