\input{../../sheet.tex}
\sbasic
\input{../equations/macros.tex}
\input{../objects/macros.tex}
\input{../sentences/macros.tex}
\input{../identity/macros.tex}
\input{../solving_equations/macros.tex}
\input{../sets/macros.tex}
\input{../set_specification/macros.tex}
\input{../functions/macros.tex}
\input{../set_equality/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../operations/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../family_operations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../common_sense/macros.tex}
\input{../injective_functions/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../algebras/macros.tex}
\input{../relations/macros.tex}
\input{../natural_summation/macros.tex}
\input{../probability/macros.tex}
\input{../cardinality/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../probability_events/macros.tex}
\input{../space/macros.tex}
\input{../real_numbers/macros.tex}
\input{../set_operations/macros.tex}
\input{../graphs/macros.tex}
\input{../real_summation/macros.tex}
\input{../probability_outcomes/macros.tex}
\input{../intervals/macros.tex}
\input{../direct_products/macros.tex}
\input{../event_probabilities/macros.tex}
\input{../probability_densities/macros.tex}
\input{../n-dimensional_space/macros.tex}
\input{../trees/macros.tex}
\input{../probability_distributions/macros.tex}
\input{../marginal_distributions/macros.tex}
\input{../conditional_event_probability/macros.tex}
\input{../multivariate_real_densities/macros.tex}
\input{../rooted_trees/macros.tex}
\input{../conditional_distributions/macros.tex}
\input{../marginal_densities/macros.tex}
\input{../rooted_tree_distributions/macros.tex}
\input{../conditional_densities/macros.tex}
\input{../rooted_tree_densities/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Tree Densities}

\ssection{Why}

We extend the definition of tree distributions to densities.

\ssection{Definition}

\ssubsection{Rooted Definition}

Let $f: \R^d \to \R$ be a density.  $f$ \t{factors according to the rooted tree}{} on $\set{1, \dots, d}$ rooted at a vertex $k$ if it can be written as a product of $f_k$ and the conditionals of $f_{i \mid j}$ for $i,j = 1, \dots, d$ and $i \neq j$ and $i \neq k$ where $j$ is the parent of $i$ in the rooted tree.

\ssubsection{Defining Result}

\begin{prop}
If a density factors according
to a tree rooted at a vertex it
factors according to that tree rooted
at any vertex.
\end{prop}

\ssubsection{Undirected Definition}

A density $f$
\t{factors according to the tree} $T$
if it factors according to the
$T$ rooted at any vertex.

\ssection{Existence and Uniqueness}

Trees are not a property of distributions,
since there is no one-to-one correspondence,
as demonstrated by the following propositions.

\ssubsection{Existence}

A distribution $f$ need not factor according to a tree.

\ssubsection{Uniqueness}
A distribution
$f$ may factor according to multiple trees.
\strats
