\input{../format.tex}
\input{../macros.tex}

\reference{sets}
\input{./macros.tex}

\begin{document}
\title{Equivalence Relations}

\section{Why}

We want to handle at once all elements which are indistinguishable or equivalent in some aspect.

\section{Definition}

Let $R$ be a relation on $A$
$R$ is an \definition{equivalence relation} if it is reflexive, symmetric, and transitive.

For an element $a \in A$, we call the set of elements in relation $R$ to $a$ the \definition{equivalence class} of $a$.
The key observation, recorded and proven below, is that the equivalence classes partition the set $A$.
A frequent technique is to define an appropriate equivalence relation on a large set $A$ and then to work with the set of equivalence classes of $A$.

We call the set of equivalence classes the \definition{quotient set} of $A$ under $R$.
An equally good name is the divided set of $A$ under $R$, but this terminology is not standard.
The language in both cases reminds us that $\sim$ partitions the set $A$ into equivalence classes.

\subsection{Notation}
If $R$ is an equivalence relation on a set $A$, we use the symbol $\sim$.
When alone, $\sim$ is read aloud as \say{sim,} but we still read $a \sim b$ aloud as \say{a equivalent to b.}
We denote the quotient set of  $A$ under $\sim$ by $A/\sim$, read aloud as \say{A quotient sim}.

\subsection{Results}

\section{Order Relations}

Here we survey a two other special relation on a set.
Let $R$ a relation on the non-empty set $A$.
We call $R$ \definition{anti-symmetric} if for two nonequal elements $a, b \in A$, $(a, b) \in R \implies (b, a) \not\in R$.
If $R$ is reflexive, transitive, and anti-symmetric then we call $R$ a \definition{partial order} on $A$.

A \definition{partially ordered set} is a set together with a partial order.
The language partial is meant to suggest that two elements need not be comparable.j
For example, suppose $R$ is $\Set{(a,a)}{a \in A}$; we may justifiably call this no order at all and call $A$ totally unordered, but it is a partial order by our definition.

Often we want all elements of the set $A$ to be comparable.
We call $R$ \definition{connexive} if for all $a, b \in A$, $(a, b) \in R$ or $(b, a) \in R$.
If $R$ is a partial order and connexive, we call it a \definition{total order}.


A \definition{totally ordered set} is a set together with a total order.
The language is a faithful guide: we can compare any two elements.
Still, we prefer one word to three, and so we will use the shorter term \definition{chain} for a totally ordered set; other terms include \definition{simply ordered set} and \definition{linearly ordered set}.

\subsection{Notation}
We denote total and partial orders on a set $A$ by $\preceq$.
We read $\preceq$ aloud as \say{precedes or equal to} and so read $a\preceq b$ aloud as \say{a precedes or is equal to b.}
If $a \preceq b$ but $a \neq b$, we write $a \prec b$, read aloud as \say{a precedes b.}

\end{document}
