\input{../../sheet.tex}
\sbasic
\input{../sets/macros.tex}
\input{../sentences/macros.tex}
\input{../set_equality/macros.tex}
\input{../set_specification/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../empty_set/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../relations/macros.tex}
\input{../objects/macros.tex}
\input{../functions/macros.tex}
\input{../identity/macros.tex}
\input{../operations/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../real_numbers/macros.tex}
\input{../intervals/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Real Functions}

\ssection{Why}

We name functions whose domain
is the real numbers.

\ssection{Definition}

A
\ct{real function}{}
is a real-valued function
The domain
is often an
interval of real
numbers, but may be any
non-empty set.

\ssubsection{Notation}

$f: \R \to \R$. $f$ is a real
function.
To speak of functions defined
on intervals,
let $a, b \in \R$.
$g: [a, b] \to \R$.
is a real function
defined on a closed interval.
$h: (a, b) \to \R$
is a real function
defined on an open interval.

We regularly declare the interval
and the function in one pass:
Let $f: [a, b] \to \R$, read
aloud as \say{$f$ from
closed $a$ $b$ to $\R$.}
Or, let $f: (a, b) \to \R$
read aloud as
\say{$f$ from open $a$ $b$ to $\R$}.

\ssection{Examples}

\begin{expl}
Let $c \in \R$.
Let $f: \R \to \R$ be such that
$f(x) = c$ for every $x \in \R$.
$f$ is a real function.
\end{expl}

\begin{expl}
\item Let $f: \R to \R$ with $f(x) = 2x^2 + 1$ for all $x \in R$.
$f$ is a real function.
\end{expl}

\begin{expl}
  Let $f: \R \to \R$ with
  \[
    f(x) = \begin{cases}
      1 & \text{ if } x \in \Q \\
      0 & \text{ otherwise. }
    \end{cases}
  \]
$f$ is a real function.
\end{expl}

\strats
