\input{../format.tex}
\input{../macros.tex}

\input{../sets/macros.tex}

\input{./macros.tex}

\begin{document}
\title{Relations}

\section{Why}
We want a precise notion for how the elements of one set relate to elements of another set, or how elements of a set relate to other elements of the same set.

\section{Definition}

A \definition{relation} between two non-empty \term{sets}{sets} $A$ and $B$ is a subset of $A \cross B$.
So then, naturally, a relation on a single set $C$ is a subset of $C \cross C$.

\subsection{Notation}
As relations are sets, our de facto protocol is to denote them by upper case capital letters, for example, the letter $R$.
Let $R$ a relation on $A$ and $B$.
If $(a, b) \in R$, we often write $a R b$, read aloud as \say{a in relation $R$ to b.}

In many cases, though, we eschew the set notation and use particular symbols.
Often the symbols we use are meant to be suggestive of the relation.
Some examples include $\sim$, $=$, $<$, $\leq$, and $\prec$.

\section{Equivalence Relations}

Here we survey a special relation on a set.
Let $R$ a relation on the non-empty set $A$.
If $aRa$, then we call $R$ \definition{reflexive}.
If $aRb$ if and only if $bRa$ then we call $R$ \definition{symmetric}.
If $aRb$ and $bRc$ together imply $aRc$, then we call $R$ \definition{transitive}.
If $R$ is reflexive, symmetric, and transitive we call it an \definition{equivalence relation}.

For an element $a \in A$, we call the set of elements in relation $R$ to $a$ the \definition{equivalence class} of $a$.
The key observation, recorded and proven below, is that the equivalence classes partition the set $A$.
A frequent technique is to define an appropriate equivalence relation on a large set $A$ and then to work with the set of equivalence classes of $A$.

We call the set of equivalence classes the \definition{quotient set} of $A$ under $R$.
An equally good name is the divided set of $A$ under $R$, but this terminology is not standard.
The language in both cases reminds us that $\sim$ partitions the set $A$ into equivalence classes.

\subsection{Notation}
If $R$ is an equivalence relation on a set $A$, we use the symbol $\sim$.
When alone, $\sim$ is read aloud as \say{sim,} but we still read $a \sim b$ aloud as \say{a equivalent to b.}
We denote the quotient set of  $A$ under $\sim$ by $A/\sim$, read aloud as \say{A quotient sim}.

\subsection{Results}

\section{Order Relations}

Here we survey a two other special relation on a set.
Let $R$ a relation on the non-empty set $A$.
We call $R$ \definition{anti-symmetric} if for two nonequal elements $a, b \in A$, $(a, b) \in R \implies (b, a) \not\in R$.
If $R$ is reflexive, transitive, and anti-symmetric then we call $R$ a \definition{partial order} on $A$.

A \definition{partially ordered set} is a set together with a partial order.
The language partial is meant to suggest that two elements need not be comparable.j
For example, suppose $R$ is $\Set{(a,a)}{a \in A}$; we may justifiably call this no order at all and call $A$ totally unordered, but it is a partial order by our definition.

Often we want all elements of the set $A$ to be comparable.
We call $R$ \definition{connexive} if for all $a, b \in A$, $(a, b) \in R$ or $(b, a) \in R$.
If $R$ is a partial order and connexive, we call it a \definition{total order}.


A \definition{totally ordered set} is a set together with a total order.
The language is a faithful guide: we can compare any two elements.
Still, we prefer one word to three, and so we will use the shorter term \definition{chain} for a totally ordered set; other terms include \definition{simply ordered set} and \definition{linearly ordered set}.

\subsection{Notation}
We denote total and partial orders on a set $A$ by $\preceq$.
We read $\preceq$ aloud as \say{precedes or equal to} and so read $a\preceq b$ aloud as \say{a precedes or is equal to b.}
If $a \preceq b$ but $a \neq b$, we write $a \prec b$, read aloud as \say{a precedes b.}

\end{document}
