\input{../../sheet.tex}
\sbasic
\input{../equations/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../sentences/macros.tex}
\input{../family_operations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../common_sense/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../length_common_notions/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../natural_summation/macros.tex}
\input{../probability/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../real_numbers/macros.tex}
\input{../distance/macros.tex}
\input{../empty_set/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../real_summation/macros.tex}
\input{../probability_outcomes/macros.tex}
\input{../intervals/macros.tex}
\input{../subset_systems/macros.tex}
\input{../objects/macros.tex}
\input{../relations/macros.tex}
\input{../families/macros.tex}
\input{../natural_addition/macros.tex}
\input{../metrics/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../set_operations/macros.tex}
\input{../probability_events/macros.tex}
\input{../probability_distributions/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../functions/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../natural_difference/macros.tex}
\input{../topological_spaces/macros.tex}
\input{../cardinality/macros.tex}
\input{../event_probabilities/macros.tex}
\input{../measures/macros.tex}
\input{../set_equality/macros.tex}
\input{../function_composites/macros.tex}
\input{../direct_products/macros.tex}
\input{../topological_sigma_algebra/macros.tex}
\input{../probability_measures/macros.tex}
\input{../measurable_functions/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sequences/macros.tex}
\input{../random_variables/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Random Variable Sigma Algebra}

\ssection{Why}

What does it mean for
two random variables to
be independent?
What are the events associated
with a random variable?
TODO

\ssection{Definition}
\ssubsection{Defining Result}

\begin{prop}

The set of inverse images
the distinguished sets
of a measurable space under
a function from a set to
that space is a sigma algebra.

If the first set and the
function are measurable,
the sigma algebra is a sub
sigma algebra of the domain
sigma algebra.

\begin{proof}
  Let $(X, \SA)$
  and $(Y, \SB)$ be
  measurable spaces.
  Let $f: X \to Y$
  be a measurable function.
  Define
  \[
    \SC := \Set*{f^{-1}(B)}{B \in \SB}.
  \]

  First,
  since $f^{-1}(Y) = X$,
  $X \in \SC$.

  Second, let $C \in \SC$.
  Then there is $B$ such that
  $C = f^{-1}(B)$.
  Then $X - C = X - f^{-1}(B) = f^{-1}(Y - B)$.
  Since $\SB$ is a sigma algebra,
  $B \in \SB, Y - B \in \SB$ and so
  $X - C \in \SC$.

  Finally, let $\seq{C} \subset \SC$.
  Then for every $n$ there exists
  a $B_n \in \SB$ so that $C_n = f^{-1}(B_n)$.
  Then:
  \[
    \union_{n} C_n = \union_n f^{-1}(B_n) = f^{-1}(\union B_n).
  \]
  Since $\SB$ is a sigma algebra,
  $\union_n B_n \in \SB$ and so $\union_{n} C_n \in \SC$.

  Since $f$ is measurable,
  $f^{-1}(B) \in \SA$ for
  every $B \in \SB$, and so $\SC \subset \SA$.
\end{proof}
\end{prop}

The sigma algebra
\ct{generated by a random variable}{}
is the sigma algebra consisting
of the inverse images of every measurable
set of the codomain.

The sigma algebra generated
by a family of random variables
is the sigma algebra generated
by the union of the sigma algebras
generated individually by each
of the random variables.

\ssubsection{Notation}

Let $(X, \SA, \mu)$ be a probability
space and $(Y, \SB)$ be a measurable
space.
Let $f: X \to Y$ be a random variable.
Denote by $\sigma(f)$ the
sigma algebra generated by $f$.

\ssection{Results}

\begin{prop}
  The sigma algebra generated
  by a family of random variables
  is the smallest sigma algebra
  for with respect to which each
  random variable is measurably.
\end{prop}
\strats
