\sinput{../sheet.tex}
\sbasic

\sinput{../sequences/macros.tex}
\sinput{../almost_everywhere/macros.tex}

\sstart

\stitle{Almost Everywhere}

\ssection{Why}

We treat properties failing
on a set of measure zero
as
though they occur everyhwere;
especially in discussions of
convergence.

\ssection{Definition}

A subset of
the base set of a measure
space is
\ct{negligible}{}
if there exists a
measurable set
with measure zero
containing
the subset.
Negligible sets
need not be
measurable.


A property holds
\ct{almost everywhere}{almosteverywhere}
with respect to a measure
on a measure space if
the set of elements
of the base set on which
the property does not hold
is negligible.

If the property holds
everywhere, it holds
almost everywhere.
In this sense
we call the
almost everywhere sense
\say{weaker}{}
than the everywhere sense.

\ssubsection{Notation}

Let
$(X, \mathcal{A}, \mu)$
be a measure space.
A set
$N \subset X$ is
negligible if there
exists $A \in \mathcal{A}$
with $N \subset A$ and
$\mu(N) = 0$.

We abbreviate almost
everywhere as \say{a.e.,}
read \say{almost everywhere}.
We say that a property
\say{holds a.e.}
If the measure $\mu$ is
not clear from context,
we say that the property
holds almost everywhere
$[\mu]$ or
$\mu$-a.e., read
\say{mu almost everywhere.}

\ssection{Examples}

Let $(X, \mathcal{A}, \mu)$
be a measure space
and let $R$ be the real numbers.

\ssubsection{Function Comparisons}

Let $f, g: X \to R$
be two functions on $X$,
not necessarily measurable.
Then $f = g$ almost everywhere
if the set of points at which the
functions disagree is
$\mu$-negligible.
Similarly, $f \geq g$ almost
everywhere if the set of points
where $f$ is less than $g$
is $\mu$-negligible.
If $f$ and $g$ are
$\mathcal{A}$-measurable, then
the sets
\[
\Set*{x \in X}{f(x) \neq g(x)}
\text{ and }
\Set*{x \in X}{f(x) < g(x)}
\]
are measurable; but they need
not be measurable otherwise.

\ssubsection{Function Limits}
Let $\seqt{f}: X \to R$ for each natural
number $n$
and let
$f: X \to R$
be a function.
The sequence $\seq{f}$
\ct{converges to $f$ almost everywhere}{convergesalmosteverywhere}
if
\[
  \Set*{x \in X}{\lim_{n} \seqt{f} \text{ does not exist, or } f(x) \neq \lim_{n} \seqt{f}}
\]
is $\mu$-negligible.
In this case, we write
\say{
$f = \lim_n \seqt{f}$
almost everywhere.}

\strats
