\input{../../sheet.tex}
\sbasic
\input{../finite_signed_measures/macros.tex}
\input{../signed_measures/macros.tex}
\input{../extended_real_numbers/macros.tex}
\input{../measures/macros.tex}
\input{../intervals/macros.tex}
\input{../real_limits/macros.tex}
\input{../set_operations/macros.tex}
\input{../cardinality/macros.tex}
\input{../subsets/macros.tex}
\input{../real_numbers/macros.tex}
\input{../real_sequences/macros.tex}
\input{../algebras/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../sets/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../sequences/macros.tex}
\input{../operations/macros.tex}
\input{../functions/macros.tex}
\input{../objects/macros.tex}
\input{../solving_equations/macros.tex}
\input{../function_composition/macros.tex}
\input{../relations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equations/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Measure Vector Space}

\ssection{Why}

If both signed measures are finite,
then their difference is always
well-defined.
Is the difference a finite signed
measure?

\ssection{Preliminary Result}

\begin{prop}
A linear combination of
finite signed measures is
a finite signed measure.
\begin{proof}
Let $(X,\SA)$ be a measurable space.
Let $\mu$ and $\nu$ be finite signed measures.
Let $R$ denote the real numbers.
Then $(\alpha\mu)(\emptyset) = \alpha \cdot \mu(\emptyset) = \alpha \cdot 0 = 0$.
Also for $\seq{A} \subset \SA$ disjoint,
$$
\begin{aligned}
  (\alpha\mu)(\union A_n) &= \alpha \mu(\union A_n)
  = \alpha \sum_{n = 1}^{\infty} \mu(A_n) \\ &= \sum_{n = 1}^{\infty} \alpha \mu(A_n) = (\alpha\mu)(A_n)
\end{aligned}
$$.

Similarly,
$(\mu + \nu)(\emptyset) = \mu(\emptyset) + \nu(\emptyset) = 0$.
And,
for $\seq{A} \subset \SA$ disjoint,
$$
\begin{aligned}
  (\mu + \nu)(\union A_n) &= \mu(\union A_n) + \nu(\union A_n)
  = \sum_{n = 1}^{\infty} \mu(A_n) +
  \sum_{n = 1}^{\infty} \nu(A_n) \\
  &= \sum_{n = 1}^{\infty} \mu(A_n) + \nu(A_n)
  = \sum_{n = 1}^{\infty} (\mu + \nu)(A_n)
\end{aligned}
$$.
\end{proof}
\end{prop}

\ssection{Main Result}

\begin{prop}
  The set of finite signed
  measures is a vector space.
  \begin{proof}
    Use the previous proposition.
    Observe that the function
    $\mu \equiv 0$ is a measure.
    and $\nu + \mu = \nu$ for
    all measures $\nu$.
  \end{proof}
\end{prop}

\ssubsection{Notation}
Denote the set of real
numbers by $R$.
We denote the vector
space of signed measures
on measurable space
$(X, \SA)$ by
by $M(X, \SA, R)$.
\strats
