\input{../../sheet.tex}
\sbasic
\input{../unordered_pairs/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../objects/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../relations/macros.tex}
\input{../identity/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../functions/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_intersections/macros.tex}
\input{../empty_set/macros.tex}
\input{../algebras/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../groups/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../natural_addition/macros.tex}
\input{../fields/macros.tex}
\input{../real_numbers/macros.tex}
\input{../natural_difference/macros.tex}
\input{../length/macros.tex}
\input{../vectors/macros.tex}
\input{../absolute_value/macros.tex}
\input{../functionals/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Norms}

\ssection{Why}

We want to measure
the size of an element
in a vector space.

\ssection{Definition}

A
\ct{norm}{norm}
is a real-valued
functional that is
(a) non-negative,
(b) definite,
(c) absolutely homogeneous,
(d) and satisifies a
triangle inequality.
The triangle inequality property
requires that the norm applied
to the sum of any two vectors
is less than the sum of the norms.

A \ct{norm space}{normspace}
is an ordered
pair: a vector space
whose field is the
real or complex numbers
and a norm on the space.
We require the vector space to
be over the
field of real or complex numbers
because of absolute
homogeneity: the absolute value of a
scalar must be defined.

\ssubsection{Notation}

Let $(X, F)$ be a vector
space where $F$ is the
field of real numbers
or the field of
complex numbers.
Let $R$ denote
the set of real numbers.
Let $f: X \to R$.
The functional $f$ is a norm
if
\begin{enumerate}
  \item $f(v) \geq 0$ for all $x \in V$
  \item $f(v) = 0$ if and only if $x = 0 \in X$.
  \item $f(\alpha x) = \abs{\alpha}f(x)$ for all $\alpha \in F$, $x \in X$
  \item $f(x + y) \leq f(x) + f(y)$ for all $x, y \in X$.
\end{enumerate}

In this case, for $x \in X$,
we denote $f(x)$ by $\norm{x}$,
read aloud \say{norm x}.
The notation follows the notation
of absolute value as a norm.
When we wish to distinguish
the norm from the absolute
value function, we may write
$\normm{x}$. In some cases,
we go further, and for a norm
indexed by some parameter $\alpha$
or set $A$ we write $\normm{x}_\alpha$
or $\normm{x}_A$.
\strats
