
%!name:norms
%!need:real_norm
%!need:functionals
%!wiki:https://en.wikipedia.org/wiki/Norm_(mathematics)

\section*{Why}

We generalize our notion of norm on real vectors to abstract vector spaces.

\section*{Definition}

A \t{norm} is a real-valued functional that is
(a) non-negative,
(b) definite,
(c) absolutely homogeneous,
(d) and satisifies a triangle inequality.
The triangle inequality property requires that the norm applied to the sum of any two vectors is less than the sum of the norms on those vectors.

A \t{normed space} (or \t{norm space}) is an ordered pair: a vector space whose field is the real or complex numbers and a norm on the space.
We require the vector space to be over the field of real or complex numbers because of absolute homogeneity: the absolute value of a scalar must be defined.

\subsection*{Notation}

Let $(X, \F )$ be a vector space where $\F $ is the field of real numbers or the field of complex numbers.
Let $f: X \to \R $.
The functional $f$ is a norm if
    \begin{enumerate}
      \item $f(v) \geq 0$ for all $x \in V$
      \item $f(v) = 0$ if and only if $x = 0 \in X$.
      \item $f(\alpha  x) = \abs{\alpha }f(x)$ for all $\alpha \in \F $, $x \in X$
      \item $f(x + y) \leq f(x) + f(y)$ for all $x, y \in X$.
    \end{enumerate}

In this case, for $x \in X$, we denote $f(x)$ by $\norm{x}$, read aloud ``norm x''.
The notation follows the notation for the absolute value function is a norm on the vector space of real numbers.
In some cases, we go further, and for a norm indexed by some parameter $\alpha $ or set $A$ we write $\norm{x}_\alpha $ or $\norm{x}_A$.

When the field is assumed or clear from context, it is succinct to say let $(V, \norm{\cdot })$ be a normed space.

\subsection*{Examples}

The absolute value function is a norm on the vector space of real numbers.
In addition, the (Euclidean norm) is a norm on the vector space $\R ^n$.

\subsection*{Other terminology}

The descriptive but slight more verbose \t{norm vector space} and \t{normed vector space} are also in usage.
