%!name:complex_numbers
%!need:real_arithmetic
%!need:absolute_value
%!refs:david_brillinger/time_series_data_analysis_and_theory/02_foundations

\ssection{Why}

We want to find the roots of negative numbers.\footnote{Future editions will modify this, and will discuss the existence of solutions of algebraic equations.}

\ssection{Definition}

A \t{complex number} is an ordered pair of real numbers.
The \t{real part} of a complex number is its first coordinate.
The \t{imaginary part} of a complex number is its second coordinate.

We can identify the imaginary numbers with no complex part (i.e., $\Set*{(a, b) \in \R^2}{b = 0}$ with $\R$ in the obvious way.
For this reason, such a complex number is sometimes referred to as a \t{purely real number}
Conversely, a complex number with zero imaginary part (i.e., an element of $\Set*{(a, b) \in \R^2}{a = 0}$) is said to be a \t{purely imaginary number}.

The \t{complex conjugate} (or \t{conjugate}) of a complex number $z$ is the complex number whose real part matches $z$ and whose imaginary part is the additive inverse of $z$.
The complex conjugate of a purely real number is the same purely real number.
In other words, the complex conjugate of a complex number with no imaginary part is the same complex number.

\ssubsection{Notation}

When treating $\R^2$ as the set of complex numbers, we denote it by $\C$.
Let $z \in \C$ with $z = (a, b)$.
The real part of $z$ is $a$ and its imaginary part is $b$.
It is universal to denote $z$ by $a + ib$, and to call $i$ an (or the) \t{imaginary number}.
Some authors use $j$, it is a matter of notation.

We denote the real part of $z$ by $\re(z)$, read \say{real of z,} and the imaginary part by $\im(z)$, read \say{imaginary of z.}
So, in particular,  $\re(z) = a$ and $\im(z) = b$.

We denote the complex conjugate of the complex number $z \in \C$ by $\Cconj{z}$.
Other common notation includes $\bar{z}$, read \say{z bar}.
If there exists $a, b \in \R$ so that $z = (a, b)$, then $\Cconj{z} = (a, -b)$.
