\input{../../sheet.tex}
\sbasic
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../set_specification/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../objects/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_intersections/macros.tex}
\input{../empty_set/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../identity/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../relations/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../functions/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../operations/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../algebras/macros.tex}
\input{../groups/macros.tex}
\input{../fields/macros.tex}
\input{../vectors/macros.tex}
\input{../linear_combinations/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Linearly Dependent Vectors}

\ssection{Why}

We want some notion building up spaces using a few vectors, and we want to pick vectors which are not redundant.
This sheet is about redundancy when you are forming linear combinations of vectors.

\ssection{Definition}


A vector is \t{linearly dependent} on a sequence of vectors if it is identical to the result of some linear combination of them.
For example, any vector is linearly independent on the singleton consisting of itself.

A sequence of vectors is \t{linearly dependent} if there is a coordinate which is linearly dependent on the sequence which is identical to the original sequence except at that coordinate, which is the zero vector.

We feel that the above definitions better capture the intuition.
The usual definition of linear dependence is given in the following proposition.
\begin{prop}
  The set of terms of a sequence of vectors is linearly dependent if and only if then there exists a nontrivial linear combination of sequence whose result is the zero vector.
  \begin{proof}

  \end{proof}

\end{prop}
A finite sequence of vectors is \t{linearly dependent} if one is identical to a nontrivial linear combination of the others.
If one can be written as a linearly combination

Two vectors, then are linearly dependent if one is a scalar multiple of the other.
The sequence $(\mathbfsf{0})$ is linearly dependent since $a_1 \mathbfsf{0} = \mathbfs{0}$ for any scalar $a_1$.

\strats
