\input{../../sheet.tex}
\sbasic
\input{../unordered_pairs/macros.tex}
\input{../empty_set/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../power_set/macros.tex}
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../relations/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../natural_addition/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../functions/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../natural_difference/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../function_composites/macros.tex}
\input{../direct_products/macros.tex}
\input{../set_specification/macros.tex}
\input{../sequences/macros.tex}
\input{../almost_everywhere/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Almost Everywhere Measurability}

\ssection{Why}

Does
convergence
almost everywhere
of a sequence of measurable
functions guarantee
measurability of the
limit function?
It does
on complete measure spaces,
and we can use this result
to \say{weaken} the hypotheses of
many theorems.

\ssection{Results}

A measure is
\ct{complete}{completemeasurespace}
if every subset of a measurable set of
measure zero is measurable.
If the measure is
complete, then every
negligible set must be
measurable.

We begin with a transitivity
property:
almost everywhere equality
of two functions
allows us to infer measurability
of one from the other.

\begin{prop}
Let $(X, \mathcal{A}, \mu)$ be a measure space
Let $f,g: X \to [-\infty, \infty]$
with $f = g$ almost everywhere.
If $\mu$ is complete
and $f$ is $\mathcal{A}$-measurable,
then $g$ is $\mathcal{A}$-measurable.
\begin{proof}
\end{proof}
\end{prop}

\begin{prop}
Let $(X, \mathcal{A}, \mu)$ be a measure space.
Let $\seqt{f}: X \to [-\infty, \infty]$ for all
natural numbers $n$
and $f: X \to [-\infty, \infty]$
with
$\seq{f}$ converging to $f$ almost everywhere.
If $\mu$ is complete and
and $\seqt{f}$ is measurable for each $n$,
then $f$ is $\mathcal{A}$-measurable.
\begin{proof}
\end{proof}
\end{prop}
\strats
