\input{../../sheet.tex}
\sbasic
\input{../unordered_pairs/macros.tex}
\input{../power_set/macros.tex}
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../relations/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../functions/macros.tex}
\input{../function_composites/macros.tex}
\input{../direct_products/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../sequences/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../real_sequences/macros.tex}
\input{../real_numbers/macros.tex}
\input{../set_operations/macros.tex}
\input{../real_limits/macros.tex}
\input{../intervals/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Extended Real Numbers}

\ssection{Why}

That some limits grow
without bound leads us
to add two elements
to the set of real numbers.

\ssection{Definition}

The set of
\ct{extended real numbers}{}
is the union of
the set of real numbers
with a set containing
two elements:
one we call
\ct{positive infinity}{}
and we call
\ct{negative infinitty}{}.

\ssubsection{Extended Arithmetic}

We extend addition to all
but one ordered pair of elements
of the new set.
The sum of any real number with
a real number is defined as before.
The sum any real number with positive
infinity is positive infinity.
The sum any real number with negative
infinity is negative infinity.
The sum of positive infinity with
positive infinity is positive infinity.
The sum of negative infinity with
negative infinity is negative infinity.
We do not define the sum of
positive infinity and negative infinity.
TODO


\ssubsection{Notation}
Let $R$ denote
the set of real numbers.
We denote the element
positive infinity by
$+\infty$ and we
denote the element
negative infinity by
$-\infty$.
The set of extended real numbers
is the set
$R \union \set{+\infty,-\infty}$.

\ssection{Intervals}

We
\strats
