\input{../../sheet.tex}
\sbasic
\input{../equations/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../objects/macros.tex}
\input{../families/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../relations/macros.tex}
\input{../sentences/macros.tex}
\input{../family_operations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../common_sense/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_equality/macros.tex}
\input{../empty_set/macros.tex}
\input{../functions/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../natural_summation/macros.tex}
\input{../probability/macros.tex}
\input{../real_numbers/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../real_summation/macros.tex}
\input{../probability_outcomes/macros.tex}
\input{../intervals/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../cardinality/macros.tex}
\input{../set_operations/macros.tex}
\input{../probability_events/macros.tex}
\input{../probability_distributions/macros.tex}
\input{../measures/macros.tex}
\input{../event_probabilities/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Probability Measures}

\ssection{Why}

We use the language of measure theory to give a mathematical model for uncertain outcomes.
TODO: probability intuition sheet.

\ssection{Definition}

A \t{probability measure} is a finite measure on a measurable space which assigns the value one to the base set.
A finite measure can always be scaled to a probability measure, so these measures are standard examples of finite measures.

A \t{probability space} is a measure space whose measure is a probability measure.
The word \t{space} is natural, since we developed measure theory partly as a generalization of volume in three-dimensional space.
The \t{outcomes} of a probability space are the elements of the base set.
The \t{set of outcomes} is the base set.
The \t{events} are the elements of the sigma algebra.

The measure in a probability space corresponds to the even probability function.

\ssubsection{Notation}

Let $(A, \SA)$ be a measurable space.
We denote the set of outcomes by $\Omega$, a mnemonic for \say{outcomes.}
We denote the sigma-algebra by $\SA$, as usual.
We denote a probability measure by $\PM$, a mnemonic for \say{probability,} and intended to remind of the event probabilty function.
Thus, we often say \say{Let $(A, \SA, \PM)$ be a probability space.}

\ssubsection{Properties}
\strats
