%!name:belongings
%!need:sets
%!need:identities

\s{Why}

We want to write about objects belonging to sets.

\s{Definition}

Let $A$ denote a set; in other words, an intangible object which has some objects as members.
Let $a$ denote an object.
Recall that if two names refer to the same object, the names are equal.
Similarly, if the object denoted by $a$ is an element of the set denoted by $A$, then we say that the former name belongs to the latter name.
We write that the name $a$ belongs to the name $A$ by $a \in A$.
% We will use a symbol
% We write $a \in A$ to mean that the object denoted by $a$ belongs
% Suppose the object denoted by $a$ is belongs to the set denoted by $A$.
% In this case, we write $a \in A$.

We read this sequence of symbols aloud as \say{a in A.}
The symbol $\in$ is a stylized lower case Greek letter $\epsilon$, which is a mnemonic for $\grave{\epsilon} \sigma \tau \acute{\iota}$ which means \say{belongs} in ancient greek.
Since in English, $\epsilon$ is read aloud \say{ehp-sih-lawn,} $\in$ is also a mnemonic for \say{element of}.
Of course, we must take care.
The first name is not an element on the second name.
Rather, the object denoted by the first name is an element of the set (object) denoted by the second name.
% We denote that an object $a$ is not an element of the set $A$ by $a \not\in A$.
% We read this notation aloud as \say{a not in A.}

% We denote

% We want to say when one object \t{belongs to} another object.
% Not as a part to a whole, but rather as a \t{member} of the object.

% Since we tend to denote objects by lower case latin letters, and we tend to think of objects and the sets they belong to, we tend to denote sets by upper case latin letters.
% For example, the letter $A$, $B$ and $C$.
% belonging to sets
We tend to denote sets by upper case latin letters: for example, $A$, $B$, and $C$.
To aid our memory, we tend to use the lower case form of the letter for an element of the set.
For example, let $A$ and $B$ denote nonempty sets.
We tend to denote by $a$ an object which is an element of $A$.
And similarly, we tend to denote by $b$ an object which is an element of $B$

\blankpage
