\input{../../sheet.tex}
\sbasic
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../set_specification/macros.tex}
\input{../functions/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_intersections/macros.tex}
\input{../empty_set/macros.tex}
\input{../surjective_functions/macros.tex}
\input{../injective_functions/macros.tex}
\input{../function_composites/macros.tex}
\input{../relations/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../function_inverses/macros.tex}
\input{../equivalence_relations/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Equivalent Sets}

\ssection{Why}

We want to talk about the size of a set.

\ssection{Definition}

Two sets are \t{equivalent} if there exists a bijection between them.

\begin{prop}
  Set equivalence in the sense defined above is an equivalence relation in the power set of a set.
\end{prop}


\begin{prop}
Every proper subset of a natural number is equivalent to some smaller natural number.
\begin{proof}
TODO induction
\end{proof}
\end{prop}
TODO: smaller defined?

\begin{prop}
A set can be equivalent to a proper subset of itself.
\end{prop}
Halmos' example here is not a bijection, though...

\begin{prop}
If $n$ is a natural number, then $n$ is not equivalent ot a proper subset of itself.
\end{prop}

\begin{prop}
A set can be equivalent to at most one natural number.
\end{prop}

\begin{prop}
The set of natural numbers is infinite.
\end{prop}

\begin{prop}
A finite set is never equivalent to a proper subset of itself.
\end{prop}

\begin{prop}
Every subset of a finite set is finite.
\end{prop}

\begin{prop}
Every subset of a natural number is equivalent to a natural number.
\end{prop}

\strats
