\input{../../sheet.tex}
\sbasic
\input{../real_convergence/macros.tex}
\input{../absolute_value/macros.tex}
\input{../real_sequences/macros.tex}
\input{../length/macros.tex}
\input{../real_numbers/macros.tex}
\input{../sequences/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../function_composition/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../solving_equations/macros.tex}
\input{../functions/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equations/macros.tex}
\input{../relations/macros.tex}
\input{../operations/macros.tex}
\input{../objects/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../sets/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Real Series}

\ssection{Why}

We want to sum infinitely
many real numbers.

\ssection{Definition}


Let $n$ be a natural number.
The $n$th
\ct{partial sum}{partialsum}
of a sequence of real numbers
is the sum of first $n$ elements
of the sequence.
The first partial sum is
the first term of the sequence.
The third partial sum
is the sum of first three
elements of the sequence.

The \ct{series}{series}
of the sequence is the
sequence of partial sums.
The sequence is
\ct{summable}{summable}
if the series converges.

Since there exist
sequences which do not
converge, there
exist sequences which
are not summable.
Consider the sequence which
alternates between $+1$ and
$-1$, and starts with $+1$.
Its series alternates between
$+1$ and $0$, and so does
not converge.

\ssubsection{Notation}

Let $\seq{a}$ be a sequence
of real numnbers. For
natural number $n$, define:
\[
s_n = \sum_{k = 1}^{n} a_k.
\]
Then $\seq{s}$ is the series
of $\seq{a}$. If the series
converges, then there exists
a real number $s$, the limit,
and we write:
\[
  s = \lim_{n\to\infty} s_n = \lim_{n\to\infty} \sum_{k = 1}^{n} a_k
\]
We read these relations aloud as
\say{s is the limit as n goes to infinity
of s n} and
\say{s is the limit as n goes to infinity
of the sum of a k from k equals 1 to n.}

To avoid referencing $s_n$, we write:
\[
  \sum_{k = 1}^{\infty} a_k = s,
\]
read aloud as the
\say{the sum from 1 to infinity
of a k is s.}
The notation is subtle, and
requires justification
by the algebra of series. TODO
\strats
