\input{../../sheet.tex}
\sbasic
\input{../objects/macros.tex}
\input{../relations/macros.tex}
\input{../sentences/macros.tex}
\input{../operations/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../functions/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_specification/macros.tex}
\input{../algebras/macros.tex}
\input{../set_equality/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../subset_systems/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../set_operations/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../cardinality/macros.tex}
\input{../measures/macros.tex}
\input{../measurable_functions/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Measurable Function Operations}

\ssection{Why}

Under which operations is
the set of measurable
functions closed?

\ssection{Overview}

Measurable functions are closed
under composition and concatenation.
Taking these facts
together with the observation
that continuous functions
are measurable, we conclude
that measurable
functions are closed under
addition, multiplication,
and (with suitable nonzero
assumptions) division.

\ssection{Results}

\begin{prop}
The composition of two
measurable functions
is measurable.
\begin{proof}
Let
$(X, \mathcal{A})$,
$(Y, \mathcal{B})$,
$(Z, \mathcal{C})$
be measurable spaces.
Let $f: X \to Y$
and $g: Y \to Z$ be
measurable functions.
Define $h = g \circ f$.

Let $C \in \mathcal{C}$.
Measurability of $g$
implies
$g^{-1}(C) \in \mathcal{B}$.
This fact, together with
measurability of $f$,
implies
$f^{-1}(g^{-1}(C)) \in \mathcal{A}$.
Since $h^{-1} = f^{-1} \circ g^{-1}$,
we conclude that
$h$ is measurable.
\end{proof}
\end{prop}

\begin{prop}
  A continuous function
  between topological
  spaces
  is measurable with
  respect to the
  topological sigma algebras.
\end{prop}

\begin{prop}
  The concatentation of
  two measurable functions
  is measurable.
  \begin{proof}
Let
$(X, \mathcal{A})$,
$(Y, \mathcal{B})$
and
$(Z, \mathcal{C})$
be measurable spaces.
Let
$f: X \to Y$
and
$g: X \to Z$
be measurable.
Define
$h: X \to Y \cross Z$
by $h(x) = (f(x), g(x))$.
  \end{proof}
\end{prop}

\begin{prop}
Let $(X, \mathcal{A})$
be a measurable space
and let $R$ denote the
real numbers.
Let
$f,g: X \to R$
be measurable.

Then, $f+g$ and $fg$ are measurable.
\end{prop}
\strats
