\input{../../sheet.tex}
\sbasic
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Set Specification}

\ssection{Why}

Can we always construct
subsets?

\ssection{Definition}

We will say that we can.
We assert that to
every set and every sentence
predicated of elements of the
set there exists a second
set (a subset of the first)
whose elements satisfy
the sentence.
It is an consequence of the axiom
of extension that this set is unique.

This is sometimes called
the \ct{axiom of specification}{}.
We call it the set obtained
from the first set by
\ct{specifying}{} elements
according to the sentence.

\ssubsection{Notation}

Let $A$ be a set.
Let $S(a)$ be a sentence.
We use the notation
\[
  \Set*{a \in A}{\;S(a)\;}
\]
to denote the subset of $A$
specified by $S$.
We read the symbol $\mid$ aloud as
\say{such that.}
We read the whole notation aloud as
\say{a in A such that...}

We call the notation
\ct{set-builder notation}{setbuildernotation}.
Set-builder notation avoids enumerating
elements.
This notation is really indispensable for
sets which have many members, too many
to reasonably write down.

\ssection{Example}

For example, let $a, b, c, d$
be distinct objects.
Let $A = \set{a, b, c, d}$.
Then
$\Set*{x \in A}{x \neq a}$
is the set $\set{b, c, d}$

Now let $B$ be an arbitrary
set.
The set $\Set*{b \in B}{b \neq b}$
specifies the empty set.
Since the statement $b \neq b$ is
false for all objects $b$.

%!TODO: russel's paradox? p 6 of halmos
\strats
