\input{../../sheet.tex}
\sbasic
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../relations/macros.tex}
\input{../functions/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Function Composition}

\ssection{Why}

We want a notion
for applying
two functions
one after the other.
We apply a first function
then a second function.

\ssection{Definition}

Consider
two functions
for which the codomain
of the first function
is the domain of the
second function.

The
\ct{composition}{composition}
of the second function with
the first function
is the function which
associates each element
in the first's domain
with the element in
the second's codomain
that the second function
associates with the
result of the first function.

The idea is that we take
an element in the first
domain.
We apply the first function
to it.
We obtain an element in the
first's codomain.
This result is an element of
the second's domain.
We apply the second function
to this result.
We obtain an element
in the second's codomain.
The composition of the second
function with the first
is the function so constructed.

\ssubsection{Notation}

Let $A, B, C$ be
non-empty sets.
Let $f: A \to B$
and $g: B \to C$.
We denote the
composition
of $g$ with $f$
by
$g \comp f$
read aloud as
\say{g composed with f.}
To make clear the domain
and comdomain, we denote
the composition
$g \comp f: A \to C$.

In previously introduced
notation,
$g \comp f$
satisfies
\[
  (g \comp f)(a) = g(f(a))
\]
for all $a \in A$.
\strats
