\input{../../sheet.tex}
\sbasic
\input{../unordered_pairs/macros.tex}
\input{../empty_set/macros.tex}
\input{../subset_systems/macros.tex}
\input{../injective_functions/macros.tex}
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../natural_addition/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../real_functions/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../cardinality/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../relations/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../natural_difference/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../partitions/macros.tex}
\input{../characteristic_functions/macros.tex}
\input{../measures/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../functions/macros.tex}
\input{../function_composites/macros.tex}
\input{../direct_products/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../simple_functions/macros.tex}
\input{../measurable_functions/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../sequences/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../simple_integrals/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../real_sequences/macros.tex}
\input{../real_numbers/macros.tex}
\input{../nonnegative_integrals/macros.tex}
\input{../set_operations/macros.tex}
\input{../real_limits/macros.tex}
\input{../intervals/macros.tex}
\input{../real_integrals/macros.tex}
\input{../extended_real_numbers/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Integrable Function Space}

\ssection{Why}

The integrable
functions are a vector
space.

\ssection{Definition}

The
\ct{integrable function space}{integrablefunctionspace}
corresponding to a measure space
is the set of real-valued functions
which are integrable with respect
to the measure.
The term space is appropriate
because this set is a
real vector space.
If we scale an integrable
function, it remains integrable.
If we add two integrable functions,
the sum is integrable.
Thus, a linear combination of
integrable functions is
integrable.
The zero function is the zero
element of the vector space.

TODO
The open question is:
what elements of our
geometric intuition can
we bring to a space of functions.
Do functions have a size?
Are certain functions near each
other?

\ssubsection{Notation}

Let $(X, \SA, \mu)$
be a measure space.
Let $R$ denote
the set of real numbers
and let $C$ denote
the set of complex numbers.

We denote set the
real-valued integrable
functions on $X$
by $\intgrbl(X, \SA, \mu, R)$,
read aloud as \say{the real integrable
functions on
the measure space X script A mu.}
We denote set the
complex-valued integrable
functions on $X$
by $\intgrbl(X, \SA, \mu, C)$,
read aloud as \say{the complex integrable
functions on
the measure space X script A mu.}
When the field is irrelevant,
we denote them by $\intgrbl(X, \SA, \mu)$,
read aloud as \say{integrable functions on
the measure space X script A mu.}
The $\SI$ is a mnemonic for \say{integrable.}
\strats
