\input{../../sheet.tex}
\sbasic
\input{../injective_functions/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../real_functions/macros.tex}
\input{../subset_systems/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../cardinality/macros.tex}
\input{../identity/macros.tex}
\input{../objects/macros.tex}
\input{../relations/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../solving_equations/macros.tex}
\input{../characteristic_functions/macros.tex}
\input{../measures/macros.tex}
\input{../set_equality/macros.tex}
\input{../sets/macros.tex}
\input{../functions/macros.tex}
\input{../function_composition/macros.tex}
\input{../direct_products/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../simple_functions/macros.tex}
\input{../measurable_functions/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../sentences/macros.tex}
\input{../operations/macros.tex}
\input{../sequences/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../simple_integrals/macros.tex}
\input{../set_specification/macros.tex}
\input{../algebras/macros.tex}
\input{../real_sequences/macros.tex}
\input{../real_numbers/macros.tex}
\input{../length/macros.tex}
\input{../nonnegative_integrals/macros.tex}
\input{../set_operations/macros.tex}
\input{../real_limits/macros.tex}
\input{../intervals/macros.tex}
\input{../absolute_value/macros.tex}
\input{../real_integrals/macros.tex}
\input{../extended_real_numbers/macros.tex}
\input{../real_integral_monotone_convergence/macros.tex}
\input{../real_integral_dominated_convergence/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Real Integral Limit Theorems}

\ssection{Why}

A vista sheet on exchanging
integrals and limits.

\ssection{Discussion}

The monotone convergence
theorem and the dominated
convergence theorem give
conditions under which
we can exchange a limit
with an integral.
Since an integral is a limit,
these theorems give conditions
under which we can exchange
limits.

We remember in exchanging
these limits that we are
really exchanging infinite
processes. It is no suprise
that this exchange does not always
make sense.
Nonetheless,
the dominated convergence
theorem gives a simple
criteria which is easy
and guarantees the desired
exchange is valid.

TODO: Structure of the theory.
Building
from the monotone convergence
for simple functions through
to the dominated convergence.
\strats
