\input{../../sheet.tex}
\sbasic
\input{../objects/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Sets}

\ssection{Why}

We want to talk
about none, one, or
several objects considered
as an abstract whole,
for which we will use
the word \textit{set}.

\ssection{Definition}

A \ct{set}{set} is an abstract
object which we think of as
several objects considered
at once.
We say that the set
\ct{contains}{}
the objects so considered.
We call these
the
\ct{members}{members} or
\ct{elements}{element} of the set.
We say that an object
contained in a set is a
\ct{member}{memberof} of or an
\ct{element}{elementof} of the set.

We call a set which contains
no objects an
\ct{empty}{empty}.
Otherwise we call a set \ct{nonempty}{nonempty}.
We call
a set which contains
only a single object a
\ct{singleton}{singleton}.
A singleton is not the
same as the object
it contains.
Besides these two cases,
we think of sets
as containing
two or more objects.

The objects a set contains
may be other sets.
This may be subtle at
first glance, but becomes
familiar with experience.

\ssubsection{Notation}

Let us tend to
denote sets by
upper case Latin letters:
for example,
$A$, $B$, and $C$.
To aid our memory,
let us tend to use the lower
case form of the letter for
an element of the set.
For example,
let $A$ and $B$ be
nonempty sets.
Let us tend to denote by
$a$ an element of $A$,
and likewise,
by $b$ an element of $B$

Let us denote that
an object $a$
is an element of a set $A$
by $a \in A$.
We read the notation
$a \in A$ aloud as \say{a in A.}
The $\in$ is a stylized
lower case Greek letter: $\epsilon$.
It is
read aloud \say{ehp-sih-lawn} and
is a mnemonic for \say{element of}.
We write $a \not\in A$, read aloud
as \say{a not in A,} if $a$ is not
an element of $A$.

Suppose a set has few elements,
and we can list them.
If we give the objects names,
then let us denote the
set by listing
the names of its elements
between braces.
For example,
let $a$, $b$, and $c$
be three distinct objects.
Denote by $\set{a, b, c}$
the set containing theses
three objects and only these
three objects.
We can further compress notation,
and denote this set of
three objects by $A$:
so, $A = \set{a, b, c}$.
Then $a \in A$,
$b \in A$, and $c \in A$.
Moreover, if $d$
is an object and
$d \in A$, then $d = a$
or $d = b$ or $d = c$.

Let $a$ be an object.
Note that
$a \neq \set{a}$.
The left hand side, $a$,
is the object $a$.
The right hand side, $\set{a}$, is
the singleton whose element
is the object $a$.
We distinguish the set
containing one element from the
element itself.

%If the elements of a set are
%so well-known that we can
%avoid ambiguity, then we can
%describe the set in English.
%To aid our memory,
%let us tend to name such sets
%mnemonically.
%For example,
%let $L$ be the set of Latin letters.

%We develop herein a language
%for specifying things by either
%listing them explicitly or
%by listing their defining properties.
\strats
