\input{../../sheet.tex}
\sbasic
\input{../objects/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../set_equality/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Set Inclusion}

\ssection{Why}

We want language for
all of the elements
of a first set being
the elements of a second set.

\ssection{Definisions}

If every element
of a first set is
an element of a
second set we say
that the first set
is a \ct{subset}{subset}
of the second set.
Conversely, we say that
second set is a
\ct{superset}{superset} of
the first set.

Every set is a subset of itself.
Similarly, every set is a
superset of itself.
Thus, if two sets are equal,
the first is a subset of the
second and the second is
a subset of the first.
Because of our definition
of set equality, the converse
is also true.

The empty set is a subset of every set,
since it has no elements and so satisfies
our definition.
Consider a set.
We call the empty set and the set itself
\ct{improper subsets}{impropersubsets}
of the set.
All other subsets we call
\ct{proper subsets}{propersubsets}.


Finally, the \ct{power set}{powerset}
of a set is the set of all subsets of that
set.
It includes the set itself and the empty set.

\ssubsection{Notation}
Let $A$ and $B$ be sets.
We denote that $A$ is a subset of $B$ by $A \subset B$.
We read the notation $A \subset B$ aloud as \say{A subset B}.

We can express the axiom of extension by
\[
  A = B \Leftrightarrow (A \subset B) \land (B \subset A)
\]
The notation $A \subset B$
is a concise symbolism for
the sentence
\say{every element of $A$ is an element of
$B$.} Or for the alternative notation
$a \in A \implies a \in B$.


We denote the power set of $A$ by $\powerset{A}$, read aloud as \say{powerset of A.}
$A \in \powerset{A}$ and $\emptyset \in \powerset{A}$.
However, $A \subset \powerset{A}$ is false.

\ssubsection{Example}

Let $a, b, c$ be distinct
objects. Let $A = \set{a, b ,c}$
and $B = \set{a, b}$. Then
$B \subset A$.
In other notation,
$B \in \powerset{A}$.
As always, $\emptyset \in \powerset{A}$
and $A \in \powerset{A}$ as well.
In this case, we can
list the elements (which are sets)
of the power set:
\[
  \powerset{A} = \set{
    \emptyset,
    \set{a},
    \set{b},
    \set{c},
    \set{a, b},
    \set{b, c},
    \set{a, c},
    \set{a, b, c}
  }.
\]

\subsection{Immediate Results}

\begin{prop}
If $A \subset B$ and $B \subset C$ then $A \subset C$.
\begin{proof}
  Let $a \in A$. Then $a \in B$ and so then $b \in C$.
  Thus $a \in C$.
\end{proof}
\end{prop}
\strats
