%!name:integer_numbers
%!need:natural_numbers
%!need:equivalence_relations

\ssection{Why}

We want to subtract numbers.\footnote{Future editions will change this why. In particular, by referencing \sheetref{inverse_elements}{Inverse Elements} and the lack thereof in $\omega$.}

\ssection{Definition}

Consider the set $\omega \times \omega$.
This set is the set of ordered pairs of $\omega$.
In other words, the ordered pairs of natural numbers.

We say that two of these ordered pairs $(a, b)$ and $(c, d)$ is \t{integer equivalent} the $a + d = b +c$.
Briefly, the intuition is that $(a, b)$ represents $a$ less $b$, or in the usual notation \say{$a - b$}.\footnote{This account will be expanded in future editions.}
So this equivalence relation says these two are the same if $a - b = c - d$ or else $a + d = b + c$.

\begin{proposition}
	Integer equivalence is an equivalence relation.\footnote{The proof is straightforward. It will be included in future editions.}
\end{proposition}

We define the \t{set of integer numbers} to be the set of equivalence classes (see \sheetref{equivalence_relations}{Equivalence Relations}) under integer equivalence on $\omega \times \omega$.
We call an element of the set of integer numbers an \t{integer number} or an \t{integer}.
We call the set of integer numbers the \t{set of integers} or \t{integers} for short.

\ssection{Notation}

We denote the set of integers by $\Z$.
If we denote integer equivalence by $\sim$ then $\Z = (\omega \times \omega)/\sim$.

