\input{../../sheet.tex}
\sbasic
\input{../objects/macros.tex}
\input{../identity/macros.tex}
\input{../sets/macros.tex}
\input{../set_equality/macros.tex}
\input{../sentences/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_specification/macros.tex}
\input{../relations/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../functions/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../function_composition/macros.tex}
\input{../direct_products/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Sequences}

\ssection{Why}

We introduce language
for the steps of an
infinite process.

\ssection{Definition}

Let $A$ be a non-empty
set.
A \ct{sequence in}{} $A$
is a function
from the natural numbers to the
set.
The \ct{$n$th term}{} of a sequence
is the result of the $n$th natural
number; it is an element of the set.

\ssubsection{Notation}

Let $A$ be a non-empty set.
$a: \N \to A$.
is a sequence in $A$.
$a(n)$ is the $n$th term.
We also denote $a$ by
$\seq{a}$ and $a(n)$ by $\seqt{a}$.

\ssection{Subsequences}

A \ct{subindex}{} is a monotonically
increasing function from and to the
natural numbers.
Roughly,
it
selects some ordered infinite
subset of natural numbers.
A \ct{subsequence}{} of a first
sequence is any second sequence
which is the composition of the
first sequence with a subindex.

\ssection{Notation}

Let $i: N \to N$ such that
$n < m \implies i(n) < i(m)$.
Then $i$ is a subindex.
Let $b = a \comp i$.
Then $b$ is a subsequence of $a$.
We denote it by
$\set{b_{i(n)}}_n$ and the $n$th
term by $b_{i(n)}$.

TODO: integrate, from direct products

If $I$ is the set of natural numbers we denote the direct product by
\[
  \product_{i = 1}^{\infty} A_{i}.
\]
We denote an element of $\product_{i = 1}^{\infty} A_{i}$ by $(a_i)$ with the understanding that $a_i \in A_i$ for all $i = 1,2,3,\dots$.
If $A_i = A$ for all $i = 1, 2, 3,\dots$, then $(a_i)$ is a sequence in $A$.
\strats
