\input{../../sheet.tex}
\sbasic
\input{../signed_measures/macros.tex}
\input{../extended_real_numbers/macros.tex}
\input{../measures/macros.tex}
\input{../intervals/macros.tex}
\input{../real_limits/macros.tex}
\input{../set_operations/macros.tex}
\input{../cardinality/macros.tex}
\input{../subsets/macros.tex}
\input{../real_numbers/macros.tex}
\input{../real_sequences/macros.tex}
\input{../algebras/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../sets/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../sequences/macros.tex}
\input{../operations/macros.tex}
\input{../functions/macros.tex}
\input{../objects/macros.tex}
\input{../solving_equations/macros.tex}
\input{../function_composition/macros.tex}
\input{../relations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equations/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Finite Signed Measures}

\ssection{Why}

For the difference of
two (signed) measures to
be well-defined, we need one
of the two to be finite.
Otherwise,
the measure of the difference
on the base set involves subtracting
$\infty$ from $\infty$.

\ssection{Definition}

A
\ct{finite}{finitesignedmeasure}
signed measure is one for
which the measure of every set
is finite.
This condition is equivalent
to the base set having finite
measure (see below).

\ssection{Result}

\begin{prop}
\label{prop:finitesignedmeasures}
A signed measure is finite
if and only if it is finite
on the base set.

\begin{proof}
Let $(X,\SA)$ be a measurable space.
Let $\mu: \SA \to \eri$ be a signed measure.
($\Rightarrow$) If $\mu$ is finite, then $\mu(X)$
is finite since $X \in \mathcal{A}$.
($\Leftarrow)$
Next, suppose $\mu(X)$ is finite.
Let $A \in \SA$.
Then $X = A \union (X - A)$,
with these sets disjoint,
so by countable additivity
of $\mu$,
$\mu(X) = \mu(A) + \mu(X - A)$.
Since $\mu(X)$ finite, $\mu(A)$
and $\mu(X - A)$ are both finite.
\end{proof}
\end{prop}
\strats
