\input{../../sheet.tex}
\sbasic
\input{../equations/macros.tex}
\input{../equation_solutions/macros.tex}
\input{../zero/macros.tex}
\input{../families/macros.tex}
\input{../objects/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../sentences/macros.tex}
\input{../natural_sums/macros.tex}
\input{../family_operations/macros.tex}
\input{../common_sense/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../length_common_notions/macros.tex}
\input{../relations/macros.tex}
\input{../set_complements/macros.tex}
\input{../set_specification/macros.tex}
\input{../operations/macros.tex}
\input{../natural_summation/macros.tex}
\input{../probability/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_equality/macros.tex}
\input{../real_numbers/macros.tex}
\input{../distance/macros.tex}
\input{../empty_set/macros.tex}
\input{../functions/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_symmetric_differences/macros.tex}
\input{../set_intersections/macros.tex}
\input{../algebras/macros.tex}
\input{../real_summation/macros.tex}
\input{../probability_outcomes/macros.tex}
\input{../intervals/macros.tex}
\input{../subset_systems/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../metrics/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../injective_functions/macros.tex}
\input{../set_operations/macros.tex}
\input{../probability_events/macros.tex}
\input{../probability_distributions/macros.tex}
\input{../subset_algebras/macros.tex}
\input{../power_set/macros.tex}
\input{../topological_spaces/macros.tex}
\input{../cardinality/macros.tex}
\input{../event_probabilities/macros.tex}
\input{../measures/macros.tex}
\input{../topological_sigma_algebra/macros.tex}
\input{../probability_measures/macros.tex}
\input{../measurable_functions/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Random Variables}

\ssection{Why}

TODO

\ssection{Definition}


A \t{random variable} is a measurable map from a probability space to a measurable space.

A \t{real-valued random variable} is a measurable map between the probability space and the set of real numbers with its topological sigma algebra.


\ssubsection{Notation}

Let $(X, \SA, \PM)$ be a probability space.
Let $(Y, \SB)$ a measurable space.
Then a random variable is a measurable function $f: X \to Y$.

Some authors denote real-valued random variables by upper case Latin letters:
for example, $X, Y, Z$.  In this case, the base probability space is denoted by $\Omega$, a mnemonic for \say{outcomes.}.
Let $(\Omega,\SA,\PM)$ be a probability space.
Let $X: \Omega \to \R$ be measurable.
Then $X$ is a real-valued random variable.

Some authors use notation for the probability of certain common sets.
Let $A \in \SB(R)$.
Let $\PM(X \in A)$ denote $\PM(X^{-1}(A))$.
These are equivalent to
\[
  \PM(\Set*{\omega \in \Omega}{X(\omega) \in A}).
\]

Next, let $Y: \Omega \to R$
a measurable function and
let $B \in \SB(R)$.
Similar to the above,
let $\PM(X \in A,Y \in B)$
denote $\PM(X^{-1}(A) \intersect Y^{-1}(B))$.
These are equivalent to
\[
  \PM(\Set*{\omega \in \Omega}{X(\omega) \in A \text{ and } Y(\omega) \in B}).
\]
\strats
