
%!name:random_variables
%!need:probability_measures
%!need:topological_sigma_algebra
%!need:measurable_functions

\section*{Definition}

A \t{random variable} is a measurable map from a probability space to a measurable space.

A \t{real-valued random variable} is a measurable map between the probability space and the set of real numbers with its topological sigma algebra.

\subsection*{Notation}

Let $(X, \mathcal{A} , \mathbfsf{P} )$ be a probability space.
Let $(Y, \mathcal{B} )$ a measurable space.
A random variable is a measurable function $f: X \to Y$.

Some authors tend to denote real-valued random variables by upper case Latin letters: for example, $X, Y, Z$.
They reserve lower case letters $x$, $y$, $z$ for the elements of the codomains of these functions.
In such cases, they often denote the set of outcomes as $\Omega $, which \sheetref{probability_measures}{we have mentioned}is a mnemonic for outcomes.

\subsection*{Special notation for common cases}

Some authors use notation for the probability of particular, common sets.
Suppose $(\Omega , \mathcal{A} , \mathbfsf{P} )$ is a probability space with $X: \Omega  \to \R $ a real-valued random variable.
Many authors use $\mathbfsf{P} (X \in A)$ (or $P(X \in A)$, no bold) to denote
\[
\mathbfsf{P} (X^{-1}(A)) = \mathbfsf{P} (\Set*{\omega  \in \Omega }{X(\omega ) \in A})
\]
where $A \in \mathcal{B} (\R )$, the Borel sigma algebra on $\R $.
We will tend to use brackets in place of parentheses for clarity.
So we will write $\mathbfsf{P} [ X \in A ]$.

Similar to the above, suppose $Y: \Omega  \to \R $ is a random variable and $B \in \mathcal{B} (\R )$.
Then we will use $\mathbfsf{P} [X \in A, Y \in B]$ to denote
\[
\mathbfsf{P} (X^{-1}(A) \cap  Y^{-1}(B)) = \mathbfsf{P} (\Set*{\omega  \in \Omega }{X(\omega ) \in A \text{ and } Y(\omega ) \in B}).
\]
Similarly for $n$ random variables $X_1, \dots , X_n: \Omega \to \R $, and Borel sets $A_1, \dots , A_n$, we will use $\mathbfsf{P} [X_1 \in A_1, \dots , X_n \in A_n]$ to denote $\mathbfsf{P} (\cap _{i = 1}^{n} X_i^{-1}(A_i))$.

\blankpage