
%!name:reproducing_kernels
%!need:complete_real_inner_product_spaces
%!need:probability_measures
%!refs:wahba1990spline/1
%!need:multivariate_normals
%!need:covariance
%!need:inner_product_linear_functional_representations
%!refs:aronszajn1950/theory

  \section*{Definition}

Let $X$ be a (nonempty) set and $k$ a field.
Let $F \subset (X \to k)$ and let $\ip{\cdot , \cdot }: F \times F \to k$ be an inner product so that $(F, \ip{\cdot ,\cdot })$ is a complete inner product space.

A \t{reproducing kernel} of $(F, \ip{\cdot ,\cdot })$ is a map $R: X \times X \to k$ satisfying (1) for every $y \in X$ the function $R(\cdot , y): X \to k$ is an element of $F$ and (2) for every $f \in F$, at every $y \in X$, $f(y) = \ip{f, R(\cdot , y)}$ (the \t{reproducing property}).

$R$ is called a \say{reproducing} kernel because of the following implication of the reproducing property.
Notice that $R(\cdot , y) \in F$.
For this reason,

\subsection*{Properties}

If a reproducing kernel exists, it is unique.

\section*{Separate sheet}

Let $X$ be nonempty (index) set.
For example, $X$ may be $\upto{N}$, $\Z $, $[0, 1]$, $\R ^d$, $\Set{x \in \R ^3}{\norm{x} \leq 1}$ (the unit sphere), or $\Set{x \in \R ^3}{\alpha  \leq \norm{x} \leq \beta }$ (the atmosphere, or volume between two concentric spheres).

A symmetric, real-valued function $k: X \times X \to \R $ of two variables is said to be \t{positive semidefinite} if for any $n \in \N  $, for any real $a_1, \dots , a_n \in \R $ and $x_1, \dots , x_n \in X$, we have
    \[
\sum_{i, j = 1}^{n} a_ia_j k(x_i, x_j) \geq 0,
    \]
and \t{positive definite} if the above holds with \say{$>$}.\footnote{Some authors use the term \say{positive definite} for our term positive semidefinite and the term \say{\t{strictly positive definite}} for our term \say{positive definite.}}

Positive semidefinite kernels are useful for the following constructive reason:

\begin{proposition}
Let $X \neq \varnothing$ be a set.
If $k: X \times X \to \R $ is positive semidefinite, then there exists a probability space $(\Omega , \C A, \mathbfsf{P} )$ and a family of zero-mean normal real-valued random variables $\set{f_x: \Omega  \to \R }_{x \in X}$ with covariance function $k$, that is,
  \[
\E  f(a)f(b) = k(a, b), \quad \text{ for all } a, b \in X.
  \]\end{proposition}
This result is known by the names \t{Kolmogorov extension theorem}, \t{Kolmogorov existence theorem}, \t{Kolmogorov consistency theorem} and \t{Daniell-Kolmogorov theorem}.
\blankpage