\input{../../sheet.tex}
\sbasic
\input{../real_numbers/macros.tex}
\input{../rational_numbers/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../solving_equations/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equations/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../operations/macros.tex}
\input{../objects/macros.tex}
\input{../functions/macros.tex}
\input{../relations/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../sets/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Intervals}

\ssection{Why}

We name and denote
subsets of the
set of real numbers
which correspond to segments
of a line.

\ssection{Definition}

Take two real numbers, with the
first less than the second.

An
\ct{interval}{interval}
is one of four sets:
\begin{enumerate}
  \item
  the set of real numbers larger
  than the first number and smaller
  than the second; we call the
  interval \ct{open}{openinterval}.

  \item
  the set of real numbers larger than
  or equal to the first number and
  smaller than or equal to the second
  number; we call the interval
  \ct{closed}{closedinterval}.

  \item
  the set of real numbers larger
  than the first number and smaller
  than or equal to the second;
  we call the interval
  \ct{open on the left}{}
  and
  \ct{closed on the right}{}.

  \item
  the set of real numbers larger
  than or equal to the first number
  and smaller than the second;
  we call the interval
  \ct{closed on the left}{}
  and
  \ct{open on the right}{}.
\end{enumerate}
If an interval is neither open
nor closed we call it
\ct{half-open}{}
or
\ct{half-closed}{}

We call the two numbers
the
\ct{endpoints}{}
of the interval.
An open interval does not
contain its endpoints.
A closed interval contains
its endpoints.
A half-open/half-closed
interval contains only one
of its endpoints.
We say that the
endpoints
\ct{delimit}{delimit}
the interval.

\ssubsection{Notation}

Let $a, b$ be two real numbers
which satisfy the relation $a < b$.

We denote the open interval from
$a$ to $b$ by $(a, b)$.
This notation, although standard,
is the same as that for ordered pairs;
no confusion arises with adequate context.

We denote the closed interval from
$a$ to $b$ by $[a, b]$.
We record the fact
$(a, b) \subset [a, b]$
in our new notation.

We denote the half-open interval
from $a$ to $b$,
closed on the right, by $(a, b]$
and the half-open interval
from $a$ to $b$,
closed on the left, by $[a, b)$.
\strats
