\input{../../sheet.tex}
\sbasic
\input{../objects/macros.tex}
\input{../sets/macros.tex}
\input{../identity/macros.tex}
\input{../unordered_pairs/macros.tex}
\input{../sentences/macros.tex}
\input{../set_equality/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{../set_specification/macros.tex}
\input{../set_inclusion/macros.tex}
\input{../relations/macros.tex}
\input{../set_unions/macros.tex}
\input{../set_intersections/macros.tex}
\input{../empty_set/macros.tex}
\input{../power_set/macros.tex}
\input{../functions/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../families/macros.tex}
\input{../natural_addition/macros.tex}
\input{../natural_order/macros.tex}
\input{../natural_families/macros.tex}
\input{../natural_difference/macros.tex}
\input{../direct_products/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Datasets}

\ssection{Why}

We want language and notation for collecting elements
from a set.

\ssection{Definition}

A \t{dataset} of size $n$ \t{in} (or \t{from}) a non-empty set $A$ is an element of the direct product $A^n$.
In other words, it is an $n$-tuple.
In the case that we speak of a dataset, we call its coordinates the records.
So, for example, we call the first coordinate the first record and the second coordinate the second record.
Of course the $i$th coordinate is the $i$th record, for $i = 1, \dots, n$.

Although the terminology dataset is standard, datasets are not sets.
Datasets, in theory and (usually) in practice, contain repeat elements.
Thus we use the single word \say{dataset.}
Had we used \say{data set,} the language would suggest that the object involved was a set.
But it is not; it is a sequence.
% TODO: next sentence is weak?
A minor other point is that \say{data} is the plural form of a latin noun, and so is analagous to saying something like \say{records set,} instead of something like \say{record set.}
For these reasons we prefer the single word dataset.

\subsection{Notation}

Let $A$ be a non-empty set.
Although we usually denote sequences by $(a_1, \dots, a_n)$, we will denote datasets by $(a^1, \dots, a^n)$; notably, using a superscript.
Often $A$ is itself a set of sequences, and so we will want to refer to the $i$th component of $a^1$ by $a^1_i$.
\strats
