%!name:ordered_pair_pathologies
%!need:ordered_pairs

\ssection{Why}

Why define ordered pairs in terms of sets?
Why not make them their own intangible object?

\ssection{Pathologies}

Notice that $a \not\in (a, b)$ and similarly $b \not\in (a, b)$.
These facts led us to use the terms first and second \say{coordinate} in \sheetref{ordered_pairs}{Ordered Pairs} rather than the term \say{element} (used in \sheetref{sets}{Sets}).
Neither $a$ nor $b$ is an element of the ordered pair $\op{a, b}$.
On the other hand, it is true that $\set{a} \in \op{a, b}$ and $\set{a, b} \in \op{a, b}$.
These facts are odd.
Should they bother us?

We chose to define ordered pairs in terms of sets so that we could reuse notions about a particular type of object (sets) that we had already developed.
We chose what we may call conceptual simplicty (reusing notions from sets) over defining a new type of object (the ordered pair) with its own primitive properties.
Taking the former path, rather than the latter is a matter of taste, really, and not a logical consequence of the nature of things.

The argument for our taste is as follows.
We already know about sets, so let's use them, and let's forget cases like $\set{a, b} \in \op{a, b}$ (called by some authors \say{pathologies}).
It does not bother us that our construction admits many true (but irrelevant) statements.
Such is the case in life.

Suppose we did choose to make the object $\op{a, b}$ primitive.
Sure, we would avoid oddities like $\set{a} \in \op{a, b}$.
And we might even get statements like $a \in \op{a, b}$ to be true.
But to do so we would have to define the meaning of $\in$ for the case in which the right hand object is an \say{ordered pair}.
Our current route avoids introducing any new concepts, and simply names a construction in already developed concepts.
