\input{../../sheet.tex}
\sbasic
\input{../complex_numbers/macros.tex}
\input{../real_integrals/macros.tex}
\input{../absolute_value/macros.tex}
\input{../real_numbers/macros.tex}
\input{../nonnegative_integrals/macros.tex}
\input{../length/macros.tex}
\input{../integer_numbers/macros.tex}
\input{../set_specification/macros.tex}
\input{../simple_functions/macros.tex}
\input{../solving_equations/macros.tex}
\input{../set_extension/macros.tex}
\input{../characteristic_functions/macros.tex}
\input{../arithmetic/macros.tex}
\input{../equations/macros.tex}
\input{../identity/macros.tex}
\input{../sets/macros.tex}
\input{../real_functions/macros.tex}
\input{../natural_numbers/macros.tex}
\input{../operations/macros.tex}
\input{../objects/macros.tex}
\input{../functions/macros.tex}
\input{../intervals/macros.tex}
\input{../relations/macros.tex}
\input{../ordered_pairs/macros.tex}
\input{./macros.tex}
\sstart
\stitle{Complex Integrals}

\ssection{Why}

TODO
We extend integrability
to complex functions.

\ssection{Definition}

A \ct{measurable}{}
complex-valued function
on a measurable space is
one whose real and imaginary
parts are both measurable.
A \ct{integrable}{}
complex-valued function
on a measurable space is
one whose real and imaginary
parts are both integrable.
called measurable if
its real and imaginary
parts are measurable.

The \ct{integral}{}
of a integrable complex-valued
function on a measurable space
is the complex number whose
real part is the integral
of the real part of the function
and whose imaginary part is the
integral imaginary part of the
function.


\ssubsection{Notation}

Let $(X, \SA, \mu)$
be a measure space.
Let $C$ denote the set
of complex numbers.
Let $f: X \to C$
be a function.
$f$ is measurable
if $\re(f)$ and $\im(f)$
are measurable.
$f$ is integrable if
$\re(f)$ and $\im(f)$
is integrable.
If $f$ is integrable,
we denote its integral
by $\int f d\mu$.
We have defined it by:
\[
  \int f d\mu = \int \re(f)d\mu
  + i\int \im(f) d\mu.
\]

\ssection{Results}

\begin{prop}
A linear combination
of two integrable complex-valued
functions is an integrable
complex-valued function.
\end{prop}

\begin{prop}
The integral is a linear
operator on the vector space
of integrable complex-valued
functions.
\end{prop}

\begin{prop}
The absolute value
of the integral of a
complex-valued function
is smaller than the integral
of the absolute value
of the function.

\begin{proof}
Let $(X, \SA, \mu)$
be a measure space.
Let $C$ denote the
complex numbers.
Let $f: X \to C$
integrable.
There exists $\alpha \in C$
with $\abs{\alpha} = 1$
such that
\[
  \abs*{\int f d\mu} = \alpha \int f d\mu.
\]
Since the integral is homogenous,
\[
  \begin{aligned}
  \abs*{\int f d\mu}
  &= \int \alpha f d\mu
  &= \int \re(\alpha f) d\mu + i \int \im(\alpha f)d\mu.
  \end{aligned}
\]
  Since $\abs*{\int f d\mu}$ is real,
  $\int \im(\alpha f) d\mu = 0$,
  so
  \[
  \begin{aligned}
  \abs*{\int f d\mu}
  &= \int \re(\alpha f) d\mu
  &\leq \int \abs*{\alpha f} d\mu
  &= \int \abs{f} d\mu,
  \end{aligned}
  \]
  since $\re(z) \leq \abs{z}$ for all
  complex numbers $z$ and $\abs{\alpha} = 1$.
\end{proof}
\end{prop}
\strats
