\input{../sheet.tex}
\sbasic

\input{../metrics/macros.tex}

\sstart

\stitle{Metrics}

\ssection{Why}

We want to talk
about the \say{closeness}
of objects in a set.

\ssection{Definition}

Our common sense notions
will be the following:
(a) close objects are not
distant
(b) distance is a positive
quantity
(a) any two distinct objects
are some discernible distance apart
(b) closeness is transitive: if one object is close
to a second object, and the second
is close to the third, then the
first is close to the third.

Two objects are close
if they are not distant.
We name a class of functions
which capture the
essence of distance
from the
plane of analytic geometry.

A
\ct{metric}{metric}
on a set
is a function
on ordered pairs of elements
of the set which
is symmetric, non-negative,
definite, and triangularly
transitive.
A \ct{metric space}{metric space}
is an ordered
pair: a set with
a metric on the set.

That the function is symmetric
is natural: the distance of
two objects should not depend
on their order.

In a metric space,
we say that one pair
of objects is \ct{closer}{closer}
together if
the metric
of the first pair
is smaller than the
metric value of the
second pair.

Thee properties
of a metric are satisfied
by the absolue value
on the real numbers and
by the usual distance
in two-dimensional real plane.

\ssubsection{Notation}

Let $A$ be a set
and let $R$ be the set
of real numbers.
We commonly denote
a metric by the letter
$d$, as a mnemonic
for \say{distance.}
Let $d: A \times A \to R$.
Then $d$ is a metric if:
\begin{enumerate}
  \item
    it is non-negative,
    which we tend to denote by
    $$
      d(a, b) \geq 0, \quad \forall a,b \in A.
    $$
    %We read this notation as:
    %\say{the distance between
    %a and b is at least zero}
  \item
    it is definite, which we tend to denote
    by
    $$
      d(a, b) = 0 \Leftrightarrow a = b, \quad \forall a,b \in A.
    $$

%    We read this notation as:
%    \say{the distance between
%    two objects is zero
%    a and b is at least zero}
  \item
    it is symmetric, which we tend to denote by:
    $$
      d(a, b) = d(b, a), \quad \forall a,b \in A.
    $$
  \item
    it is triangularly transitive, which we tend to
    denote by
    $$
      d(a, b) \leq d(a, c) + d(c, b), \quad \forall a,b,c \in A.
    $$
\end{enumerate}
As usual, we denote the metric space
of $A$ with $d$ by
$(A, d)$.


\strats
